### 2024-03-10 outputs/paper/paper.qmd
download data script

---
title: ""
title-block-banner: true
abstract: ""
thanks: "Code and data supporting this analysis are available at https://github.com/TEJMaster/Replication-For-Money-Illusion.git Replication on Social Science Reproduction platform available at: https://www.socialsciencereproduction.org/reproductions/1671/published/index"
author: "Terry Tu, Jingyi Shen, Yaning Jin "
date: today
date-format: long
format: pdf
toc: true
toc-depth: 1
number-sections: true
bibliography: references.bib
link-citations: true
editor: 
  markdown: 
    wrap: sentence
---

### 2024-03-10 scripts/01-download_data.R

@@ -1,0 +1,32 @@
+# Load necessary packages
+library(opendatatoronto)
+library(readr)
+library(dplyr)
+library(here)
+
+# Set the root directory for the 'here' package
+# This is typically the top-level directory of your project
+set_here <- here::set_here()
+
+# Search for packages related to "building evaluation"
+search_result <- search_packages("building evaluation")
+
+# The first row is the desired dataset
+# Extract the dataset ID (4ef82789-e038-44ef-a478-a8f3590c3eb1)
+dataset_id <- "4ef82789-e038-44ef-a478-a8f3590c3eb1"
+
+# List all resources available for the dataset
+resources <- list_package_resources(dataset_id)
+
+# Assuming you want to download the first resource
+# You can modify the index if you want a different resource
+resource_id <- resources$id[1]
+
+# Download the resource
+building_evaluation_data <- get_resource(resource_id)
+
+# Save the data to a CSV file in the 'inputs/data' directory
+write_csv(building_evaluation_data, here("inputs", "data", "building_evaluation_data.csv"))
+
+# Print a message indicating completion
+cat("Data has been downloaded and saved as 'building_evaluation_data.csv' in the 'inputs/data' directory")

### 2024-03-11 outputs/paper/paper.qmd
model

@@
 abstract: ""
-thanks: "Code and data supporting this analysis are available at https://github.com/TEJMaster/Replication-For-Money-Illusion.git Replication on Social Science Reproduction platform available at: https://www.socialsciencereproduction.org/reproductions/1671/published/index"
+thanks: "Code and data supporting this analysis are available at "
 author: "Terry Tu, Jingyi Shen, Yaning Jin "
@@
 ---
+
+```{r setup, include=FALSE, message=FALSE}
+## Import necessary libraries
+library(ggplot2)
+library(dplyr)
+library(tidyverse)
+library(here)
+library(readr)
+```
+
+## Introduction
+
+## Data
+
+```{r include=FALSE, message=FALSE}
+# read the data file and store it in the 'data' variable
+data <- read_csv(here("outputs", "data", "cleaned_building_data.csv"))
+```
+
+## Model
+
+## Result
+
+## Discussion

### 2024-03-11 scripts/01-download_data.R

@@ -4,10 +4,6 @@ library(readr)
 library(dplyr)
 library(here)
 
-# Set the root directory for the 'here' package
-# This is typically the top-level directory of your project
-set_here <- here::set_here()
-
 # Search for packages related to "building evaluation"
 search_result <- search_packages("building evaluation")
 

### 2024-03-11 scripts/02-cleanup-data.R

@@ -1,0 +1,16 @@
+# Load necessary packages
+library(readr)
+library(dplyr)
+library(here)
+
+# Load your existing data file into a data frame
+data <- read_csv(here("inputs", "data", "building_evaluation_data.csv"))
+
+# Clean up the data by filtering out NAs in YEAR.BUILT and YEAR.EVALUATED
+# and then adding the 'AGE' column
+cleaned_data <- data %>%
+  filter(!is.na(YEAR.BUILT) & !is.na(YEAR.EVALUATED)) %>%
+  mutate(AGE = YEAR.EVALUATED - YEAR.BUILT)
+
+# Save the cleaned data to a CSV file in the 'outputs/data' directory
+write_csv(cleaned_data, here("outputs", "data", "cleaned_building_data.csv"))

### 2024-03-11 outputs/paper/paper.qmd
added new scripts

@@
 ---
-title: ""
+title: "Building Integrity in Retrospect: Assessing the Impact of Age on 2023 Safety Evaluations"
 title-block-banner: true
@@
 # read the data file and store it in the 'data' variable
-data <- read_csv(here("outputs", "data", "cleaned_building_data.csv"))
+cleaned_data <- read_csv(here("outputs", "data", "cleaned_building_data.csv"))
 ```
@@
 
+```{r echo=FALSE}
+# Construct a linear model
+lm_model <- lm(CURRENT.BUILDING.EVAL.SCORE ~ AGE, data = cleaned_data)
+
+# Summary of the linear model
+summary(lm_model)
+```
+```{r echo=FALSE}
+# Create a scatter plot with a regression line to visualize the relationship
+improved_plot <- ggplot(cleaned_data, aes(x = AGE, y = CURRENT.BUILDING.EVAL.SCORE)) +
+  geom_point(alpha = 0.5, size = 1.5) +  # Adjust transparency and size of points
+  geom_smooth(method = "lm", color = "blue", size = 1) +  # Change the size of the regression line
+  labs(
+    x = "Age of Building",
+    y = "Current Building Evaluation Score",
+    title = "Relationship between Building Age and Evaluation Score"
+  ) +
+  theme_minimal() +  # Use a minimal theme
+  theme(
+    plot.title = element_text(face = "bold", hjust = 0.5, size = 16),
+    axis.title = element_text(size = 14),
+    axis.text = element_text(size = 12),
+    legend.position = "none"  # Hide the legend if not necessary
+  )
+
+# Print the improved plot
+print(improved_plot)
+```
+
 ## Discussion

### 2024-03-12 outputs/paper/paper.qmd
added writting

--- 2024-03-11 outputs/paper/paper.qmd
@@
 ---
-title: ""
+title: "Building Integrity in Retrospect: Assessing the Impact of Age on 2023 Safety Evaluations"
 title-block-banner: true
-abstract: ""
-thanks: "Code and data supporting this analysis are available at "
+abstract: "This study harnesses a dataset from the Toronto Open Data portal, comprising 3,435 records of apartment evaluations, to analyze the correlation between building age and safety scores.
+Employing a linear regression model, we discovered a significant inverse relationship, highlighting that older buildings tend to have lower safety evaluations.
+The findings suggest a need for policy reform, particularly in the maintenance and inspection of Toronto's aging residential infrastructure.
+Despite the study’s focus on building age, further research considering additional variables could offer a more comprehensive understanding of factors influencing building safety."
+thanks: "Code and data supporting this analysis are available at https://github.com/TEJMaster/Toronto-Building-Safety-Analysis-2023.git"
 author: "Terry Tu, Jingyi Shen, Yaning Jin "
@@
 
+In the wake of the catastrophic collapse of an aged condominium in South Florida in June 2021, which resulted in 98 casualties, a subsequent lawsuit by the bereaved families underscored the notion that routine inspections and maintenance could have forestalled the disaster[@Anderson_2021].
+This incident precipitates our investigation into forecasting the building evaluation scores for Toronto residences in 2023 via a simple linear regression model.
+An analysis was conducted on the apartment building evaluation dataset obtained from the City of Toronto's open data portal to assess the relationship between the age of a property and its evaluation score assigned by the city.
+Our research is singularly focused on elucidating the effect of one independent variable—building age—on the dependent variable, which in this context is the building evaluation score.
+
+Using simple linear regression analysis enables a detailed exploration of the linear relationship between the age of a building and its evaluation score.
+By quantifying this relationship through regression coefficients, we aim to reveal the expected change in evaluation scores for each incremental year in building age.
+The statistical significance of the age variable on evaluation scores will be ascertained using p-values.
+Provided the model satisfies the underlying assumptions, t-tests will be applied to test the hypotheses, while confidence and prediction intervals will be leveraged to quantify the effect size and enhance the accuracy of our forecasts, respectively.
+
 ## Data
@@
 # read the data file and store it in the 'data' variable
-data <- read_csv(here("outputs", "data", "cleaned_building_data.csv"))
+cleaned_data <- read_csv(here("outputs", "data", "cleaned_building_data.csv"))
 ```
+
+In this research, we examine apartment data sourced from the Toronto Open Data portal.
+The dataset encompasses 3,435 records, focusing on specific variables: the ward of each apartment, its evaluation score, and the construction year.
+The data covers evaluations across Toronto's 25 wards, with scores varying between a minimum of 0 and some achieving the maximum score of 100.
+The study includes apartments that are over three stories in height and contain at least 10 units.
+These apartments span a wide range of construction years, from as early as 1805 to as recent as 2023.
+All the apartments in this dataset adhere to the City's Apartment Building Standards bylaw, which is designed to safeguard the interests and safety of both landlords and tenants by mandating these evaluations [@Toronto_2023].
+
+### Variable Description
+
+CURRENT BUILDING EVAL SCORE: The Current Building Evaluation Score represents a measure of a building's adherence to property standards.
+This score is derived by summing two components: the current reactive score, which reflects the compliance based on any outstanding Orders and Notices of Violations, and the proactive building score, which is based on the most recent comprehensive evaluation of the building.
+
+YEAR BUILT:	This indicates the year when the building was initially constructed, sourced from Building Owners/Managers.
+
+YEAR EVALUATED: This denotes the year in which the building underwent evaluation, reflecting its condition and performance.
+
+AGE: In this research, neither YEAR BUILT nor YEAR EVALUATED was used directly, we have generated a new variable called AGE which use YEAR EVALUATED minus YEAR BUILT.
+
+### Data Analysis Tools
+
+The data analysis was performed using R [@r], a powerful open-source statistical programming language.
+Key packages from the tidyverse collection [@rTidyverse] were employed to streamline data manipulation, visualization, and analysis processes.
+These packages include ggplot2 [@rGgplot2] for creating advanced graphics, dplyr [@rDplyr] for data manipulation, readr [@rReadr] for its robust data reading functionality, here [@R-here] is used to avoid file path issue, and knitr [@rKnitr] for dynamic report generation.
+
+### Data Exportation
+
+After cleaning, the modified dataset, now stored in the `cleaned_data` data frame, is written to a new CSV file named 'cleaned_building_data.csv'.
+This file is saved in the 'outputs/data' directory, which is again constructed using the `here` function for path management.
+Saving the cleaned dataset allows for a stable version of the dataset to be used for analysis or sharing, ensuring reproducibility of results.
+
+Statistically, this script is preparing the dataset for analysis by ensuring the integrity and relevance of the data, which is foundational for any reliable statistical analysis.
+By creating the 'AGE' column, the script enables researchers to analyze the relationship between the age of a building and other variables of interest, such as compliance with property standards, in a quantitative manner.
 
@@
 
+```{r echo=FALSE}
+# Construct a linear model
+lm_model <- lm(CURRENT.BUILDING.EVAL.SCORE ~ AGE, data = cleaned_data)
+```
+
+### Coefficient
+
+```{r echo=FALSE}
+# Extract coefficients from the model
+coefficients <- summary(lm_model)$coefficients
+coefficients
+```
+
+Intercept: The intercept  \beta_0 an estimated value of 93.62182.
+This is the expected value of the response when the independent variable x is zero.
+The standard error of the intercept is 0.64813, indicating the average distance that the observed values fall from the regression line.
+
+AGE: The coefficient for AGE is -0.10086 which in terms of  \beta_1 is -0.10086.
+This suggests that for each additional year of age, the response decreases by approximately 0.10086 points, on average.
+The standard error of this estimate is 0.01015, which is a measure of the precision of the estimate.
+
+T-value: The t-value is a measure of how many standard deviations the coefficient is away from zero.
+For the intercept, the t-value is 144.449, and for AGE, it is -9.934.
+These are calculated by dividing the estimate by the standard error.
+The high absolute value of the t-statistics suggests that the coefficients are significantly different from zero.
+
+P-value: The p-value tests the null hypothesis that the coefficient is equal to zero.
+A p-value less than 0.05 typically suggests that there is a statistically significant association between the predictor and the response variable.
+In this table, both p-values are shown as "2e-16", which is a notation for a number very close to zero and indicates that both the intercept and the AGE predictor have p-values much lower than 0.05, making them highly significant.
+
+In summary, the linear regression analysis suggests that there is a statistically significant inverse relationship between the age of an apartment and its evaluation score.
+The older the apartment, the lower its evaluation score tends to be, holding other factors constant.
+The intercept indicates that a newly built apartment (AGE = 0) would have a predicted evaluation score of 93.62182.
+
+### Residuals
+
+```{r echo=FALSE}
+# Extract residuals from the model
+residuals <- resid(lm_model)
+summary(residuals)
+```
+
+1.
+Minimum Residual: This value suggests the presence of at least one observation where the building evaluation score was underestimated by the model by as much as 69.662 points, given the age of the building.
+This could be an outlier or may indicate a building whose score is exceptionally low compared to what the model predicts for its age.
+
+2.
+First Quartile Residual: 25% of the residuals are less than this value.
+It implies that a quarter of the buildings have evaluation scores that are 4.364 points less than the predicted score by the model for buildings of their respective ages.
+
+3.
+Median Residual: The median of the residuals is slightly above zero, indicating that the distribution of errors is not perfectly symmetrical and that there may be a slight tendency for the model to overestimate the scores, on average, for the buildings in this sample.
+
+4.
+Third Quartile Residual: This is the median of the upper half of the residuals.
+75% of the buildings have evaluation scores within 5.833 points of the model's prediction or better, reflecting that for the majority, the model's predictions are quite close to the actual scores.
+
+5.
+Maximum Residual: The largest positive residual suggests that the model overestimated the building evaluation score for at least one building by as much as 15.859 points compared to its actual score.
+This again may indicate an outlier or a building that performed unexpectedly well despite its age.
+
+These residuals are crucial for assessing the adequacy of the model fit and the validity of its assumptions, such as linearity, homoscedasticity (constant variance of residuals), and normality of error terms.
+The range and distribution of these residuals, particularly the presence of significant outliers, can influence the conclusions drawn from t-tests and the calculated confidence and prediction intervals.
+Such anomalies warrant further investigation into the specific characteristics of those buildings to understand why the model's predictions differ markedly from the observed scores.
+It's also important to ensure that the regression assumptions hold since this affects the validity of the p-values and confidence intervals used to quantify and infer the effect of building age on evaluation scores.
+
+### Plot for the linear model
+```{r echo=FALSE, warning=FALSE, message=FALSE}
+# Create a scatter plot with a regression line to visualize the relationship
+improved_plot <- ggplot(cleaned_data, aes(x = AGE, y = CURRENT.BUILDING.EVAL.SCORE)) +
+  geom_point(alpha = 0.5, size = 1.5) +  # Adjust transparency and size of points
+  geom_smooth(method = "lm", color = "blue", size = 1) +  # Change the size of the regression line
+  labs(
+    x = "Age of Building",
+    y = "Current Building Evaluation Score",
+    title = "Relationship between Building Age and Evaluation Score"
+  ) +
+  theme_minimal() +  # Use a minimal theme
+  theme(
+    plot.title = element_text(face = "bold", hjust = 0.5, size = 16),
+    axis.title = element_text(size = 14),
+    axis.text = element_text(size = 12),
+    legend.position = "none"  # Hide the legend if not necessary
+  )
+
+# Print the improved plot
+print(improved_plot)
+```
+
+The graph provided illustrates the findings of a simple linear regression analysis that seeks to clarify the influence of one independent variable, building age, on the dependent variable, the building evaluation score.
+The scatterplot displays individual data points representing apartments, with the age of the building on the x-axis and the current building evaluation score on the y-axis.
+
+A linear regression line has been fitted through the data, represented by the solid blue line, which indicates the average trend in the data.
+The slope of this line is a graphical representation of the regression coefficient associated with building age.
+In statistical terms, the slope tells us the average change in the evaluation score for each year increase in building age.
+If the slope is negative, it would suggest that, on average, older buildings tend to have lower evaluation scores.
+The density of the data points is heaviest near the younger age of buildings, and as age increases, the data points disperse more.
+This could suggest that there is greater variability in the scores of older buildings or that there are simply fewer older buildings in the dataset.
+
+Statistical significance is often determined by looking at the p-value for the slope of the regression line.
+In previous discussions, a p-value well below the threshold of 0.05 was mentioned, indicating that the effect of building age on evaluation score is indeed statistically significant.
+This would mean that there is a very low probability that the observed relationship, or one more extreme, would occur if there were actually no relationship between building age and evaluation score in the population.
+
+It is also important to examine the residuals, or the differences between the observed scores and those predicted by the model, which should be randomly dispersed without pattern if the model's assumptions hold true.
+In addition, the graph should be assessed for homoscedasticity, meaning that the variance of the residuals is constant across all levels of the independent variable.
+If the residuals fan out or form a funnel shape as building age increases, this would indicate heteroscedasticity, a violation of one of the linear regression assumptions, which could affect the reliability of the model.
+
+To summarize, this graph presents a visual and statistical summary of the relationship between building age and evaluation score, with the analysis revealing that age is a significant predictor of evaluation score, though it accounts for a relatively small portion of the variability in scores.
+Further analysis would be necessary to better understand the dispersion of scores, especially among older buildings, and to examine the model's underlying assumptions.
+
 ## Discussion
+
+### Overview of the Study
+
+This paper presented a detailed analysis using simple linear regression to investigate the impact of building age on the evaluation scores assigned by the City of Toronto.
+By analyzing data from the Toronto Open Data portal, the study aimed to forecast evaluation scores for Toronto residences in 2023.
+The analysis revealed a statistically significant inverse relationship between building age and evaluation score, suggesting that older buildings tend to have lower evaluation scores.
+
+### Insights into Urban Development and Maintenance
+
+One key insight from this study is the importance of building age in the overall health and safety of urban residential environments.
+The findings underscore the potential risks associated with older buildings, which may not meet modern standards or may have deteriorated over time.
+This knowledge emphasizes the need for regular inspections, maintenance, and upgrades to older buildings to ensure they remain safe and habitable.
+Additionally, the study highlights the value of continuous monitoring and evaluation by urban authorities to maintain and improve housing standards across the city.
+
+### Policy Implications and Housing Quality
+
+Another significant insight relates to the policy implications for housing quality and safety standards.
+The correlation between building age and lower evaluation scores may prompt policymakers to reconsider regulations surrounding building inspections, maintenance schedules, and renovation requirements.
+It suggests an opportunity for targeted interventions in older buildings to prevent potential hazards and improve living conditions for residents.
+Moreover, these findings could guide urban planning strategies, prioritizing the revitalization of aging housing stock and ensuring equitable access to safe and quality housing.
+
+### Limitations of the Study
+
+Despite its contributions, this study has several limitations.
+Firstly, the model accounts for only a small fraction of the variability in evaluation scores, indicating that other factors besides building age significantly influence these scores.
+The exclusion of variables such as building materials, design, maintenance history, and location may limit the comprehensiveness of the findings.
+Additionally, the model's assumptions (e.g., linearity and homoscedasticity) and the presence of outliers suggest caution in generalizing the results without further investigation.
+
+### Future Directions
+
+Given the limitations and the insights gained, future research should aim to incorporate additional variables that could affect building evaluation scores.
+A more comprehensive model including factors like renovation history, compliance with current building codes, and socio-economic characteristics of the neighborhood could provide a deeper understanding of what influences building evaluation scores.
+Longitudinal studies could also shed light on the trends over time, offering insights into the effectiveness of policy interventions and maintenance practices.
+Moreover, comparative analyses across different cities or countries could highlight unique challenges and best practices in building maintenance and safety standards.
+
+In conclusion, while this study has provided valuable insights into the impact of building age on evaluation scores, it also opens the door for further research to explore the multifaceted nature of building quality and safety.
+Addressing these questions is crucial for developing effective strategies to improve urban living conditions and ensure the longevity and safety of the housing stock.
+
+## References

### 2024-03-12 scripts/03_test-data-validity.R

@@ -1,0 +1,31 @@
+# Load necessary packages
+library(readr)
+library(dplyr)
+library(here)
+library(testthat)
+
+# Load the cleaned data file into a data frame
+data <- read_csv(here("outputs", "data", "cleaned_building_data.csv"))
+
+# Define a function to perform the tests
+perform_data_tests <- function(data) {
+  # Test if AGE column has no negative values
+  test_that("AGE column contains no negative values", {
+    expect_true(all(data$AGE >= 0), info = "There are negative values in the AGE column")
+  })
+  
+  # Test if YEAR.BUILT, YEAR.EVALUATED, CURRENT.BUILDING.EVAL.SCORE have no NA values
+  test_that("No NA values in YEAR.BUILT, YEAR.EVALUATED, CURRENT.BUILDING.EVAL.SCORE", {
+    expect_true(all(!is.na(data$YEAR.BUILT)), info = "There are NA values in YEAR.BUILT")
+    expect_true(all(!is.na(data$YEAR.EVALUATED)), info = "There are NA values in YEAR.EVALUATED")
+    expect_true(all(!is.na(data$CURRENT.BUILDING.EVAL.SCORE)), info = "There are NA values in CURRENT.BUILDING.EVAL.SCORE")
+  })
+  
+  # Test if CURRENT.BUILDING.EVAL.SCORE column has no negative values
+  test_that("CURRENT.BUILDING.EVAL.SCORE column contains no negative values", {
+    expect_true(all(data$CURRENT.BUILDING.EVAL.SCORE >= 0), info = "There are negative values in CURRENT.BUILDING.EVAL.SCORE")
+  })
+}
+
+# Run the tests on the data
+perform_data_tests(data)

### 2024-03-13 paper/paper.qmd
Structure update, added model

--- 2024-03-12 outputs/paper/paper.qmd
@@
 # read the data file and store it in the 'data' variable
-cleaned_data <- read_csv(here("outputs", "data", "cleaned_building_data.csv"))
+cleaned_data <- read_csv(here("data", "analysis_data", "cleaned_building_data.csv"))
 ```
@@
 
+The objective of our model is dual: to discern the relationship between building age and safety evaluation scores and to quantify this relationship's strength and direction.
+The study utilizes a simple linear regression model to analyze the dataset obtained from the Toronto Open Data portal.
+
+### Model set-up
+
+Let $y_i$ represent the safety evaluation score for each building. The building's age is denoted by $x_i$.The model is defined as follows:
+
+\begin{align}
+y_i &\sim \mbox{Normal}(\mu_i, \sigma) \\
+\mu_i &= \beta_0 + \beta_1 \times \mbox{AGE}_i \\
+\beta_0 &\sim \mbox{Normal}(90, 10) \\
+\beta_1 &\sim \mbox{Normal}(-0.1, 0.05)
+\end{align}
+
+The model is executed in R using the lm function. We select normal priors for the intercept and slope based on initial exploratory data analysis.
+
+### Model justification
+
+A negative coefficient for AGE is anticipated, hypothesizing that older buildings may have lower safety scores due to factors such as wear and deterioration over time.
+We anticipate the intercept to represent the evaluation score for a newly built property, with the slope capturing the average yearly decrease in score.
+
 ## Result
@@
 ```{r echo=FALSE}
-# Construct a linear model
-lm_model <- lm(CURRENT.BUILDING.EVAL.SCORE ~ AGE, data = cleaned_data)
+# Retrieve the linear model from the saved .rds file
+lm_model <- readRDS(file = here("models", "linear_model.rds"))
 ```
 
-### Coefficient
+### Model Coefficients Interpretation
 
@@
 ```
+The regression model provides two key coefficients to understand the relationship between building age and the evaluation score:
 
-Intercept: The intercept  \beta_0 an estimated value of 93.62182.
-This is the expected value of the response when the independent variable x is zero.
-The standard error of the intercept is 0.64813, indicating the average distance that the observed values fall from the regression line.
+**Intercept** ($\beta_0$)  
+The model estimates the intercept, $\beta_0$, to be 93.61663.
+This is the predicted evaluation score for a building at the time it is newly constructed, where AGE equals zero.
+Accompanied by a standard error of 0.64805, this coefficient's estimate signals the level of precision with which we can predict the evaluation score for new buildings.
+The t-value associated with the intercept is 144.459, which is highly significant, as indicated by the p-value of practically zero.
+This signifies a very strong statistical assurance in the intercept's estimate.
 
-AGE: The coefficient for AGE is -0.10086 which in terms of  \beta_1 is -0.10086.
-This suggests that for each additional year of age, the response decreases by approximately 0.10086 points, on average.
-The standard error of this estimate is 0.01015, which is a measure of the precision of the estimate.
+**Slope** ($\beta_1$)  
+The slope of the model, $\beta_1$, is determined to be -0.10079.
+This value quantifies the expected change in the building evaluation score for each additional year of age; specifically, the score is projected to decrease by about 0.10079 points annually.
+The standard error of 0.01015 suggests high precision in this estimation.
+The t-value of -9.929 reaffirms the reliability of this coefficient, with a corresponding p-value of 1.226807e-22, far below the 0.05 threshold, confirming the impact of age on evaluation scores is statistically significant.
 
-T-value: The t-value is a measure of how many standard deviations the coefficient is away from zero.
-For the intercept, the t-value is 144.449, and for AGE, it is -9.934.
-These are calculated by dividing the estimate by the standard error.
-The high absolute value of the t-statistics suggests that the coefficients are significantly different from zero.
+These coefficients paint a picture of gradual decline in building quality as measured by the evaluation scores over time.
+The statistical significance of both coefficients assures us that the model's predictions are based on real effects and not on random fluctuations within the dataset.
+This analysis emphasizes the need for rigorous maintenance and periodic updates to older buildings to preserve their integrity and safety.
 
-P-value: The p-value tests the null hypothesis that the coefficient is equal to zero.
-A p-value less than 0.05 typically suggests that there is a statistically significant association between the predictor and the response variable.
-In this table, both p-values are shown as "2e-16", which is a notation for a number very close to zero and indicates that both the intercept and the AGE predictor have p-values much lower than 0.05, making them highly significant.
+### Model Equation
 
-In summary, the linear regression analysis suggests that there is a statistically significant inverse relationship between the age of an apartment and its evaluation score.
-The older the apartment, the lower its evaluation score tends to be, holding other factors constant.
-The intercept indicates that a newly built apartment (AGE = 0) would have a predicted evaluation score of 93.62182.
+\begin{align}
+y_i &\sim \mbox{Normal}(\mu_i, \sigma) \\
+\mu_i &= \beta_0 + \beta_1 \times \mbox{AGE}_i \\
+\beta_0 &= 93.6166 \\
+\beta_1 &= -0.1008
+\end{align}
 
-### Residuals
+In this model, $y_i$ represents the predicted evaluation score for the $i$-th building, $\mu_i$ is the mean of the normal distribution for the $i$-th observation, $\beta_0$ is the intercept, and $\beta_1$ is the slope representing the change in evaluation score per year of building age.
+
+### Analysis of Residuals
 
@@
 
-1.
-Minimum Residual: This value suggests the presence of at least one observation where the building evaluation score was underestimated by the model by as much as 69.662 points, given the age of the building.
-This could be an outlier or may indicate a building whose score is exceptionally low compared to what the model predicts for its age.
+**1.
+Minimum Residual**: The minimum residual is -69.662, indicating that there is at least one building for which the model's predicted evaluation score was lower than the actual score by approximately 69.662 points.
+This could be an outlier or a building with exceptional characteristics not captured by the model.
 
-2.
-First Quartile Residual: 25% of the residuals are less than this value.
-It implies that a quarter of the buildings have evaluation scores that are 4.364 points less than the predicted score by the model for buildings of their respective ages.
+**2.
+First Quartile Residual**: The first quartile (Q1) of the residuals is -4.364, meaning that 25% of the buildings have evaluation scores that are less than 4.364 points below the model's prediction for their age.
 
-3.
-Median Residual: The median of the residuals is slightly above zero, indicating that the distribution of errors is not perfectly symmetrical and that there may be a slight tendency for the model to overestimate the scores, on average, for the buildings in this sample.
+**3.
+Median Residual**: The median residual is 1.702, suggesting a slight positive bias in the model's predictions, as the median of the error distribution is above zero.
+This indicates that, on average, the model tends to slightly overestimate the evaluation scores.
 
-4.
-Third Quartile Residual: This is the median of the upper half of the residuals.
-75% of the buildings have evaluation scores within 5.833 points of the model's prediction or better, reflecting that for the majority, the model's predictions are quite close to the actual scores.
+**4.
+Third Quartile Residual**: The third quartile (Q3) is 5.833, indicating that 75% of the buildings have evaluation scores within 5.833 points of the model's predictions or better.
+This shows that the model provides reasonably accurate predictions for the majority of buildings.
 
-5.
-Maximum Residual: The largest positive residual suggests that the model overestimated the building evaluation score for at least one building by as much as 15.859 points compared to its actual score.
-This again may indicate an outlier or a building that performed unexpectedly well despite its age.
+**5.
+Maximum Residual**: The maximum residual is 15.859, suggesting that there is at least one building for which the model's predicted evaluation score was higher than the actual score by approximately 15.859 points.
+This could be another outlier or a building that performed exceptionally well.
 
-These residuals are crucial for assessing the adequacy of the model fit and the validity of its assumptions, such as linearity, homoscedasticity (constant variance of residuals), and normality of error terms.
-The range and distribution of these residuals, particularly the presence of significant outliers, can influence the conclusions drawn from t-tests and the calculated confidence and prediction intervals.
-Such anomalies warrant further investigation into the specific characteristics of those buildings to understand why the model's predictions differ markedly from the observed scores.
-It's also important to ensure that the regression assumptions hold since this affects the validity of the p-values and confidence intervals used to quantify and infer the effect of building age on evaluation scores.
+**Interpretation**: The residuals provide insights into the model's fit and the distribution of errors.
+The presence of outliers and the distribution's slight asymmetry warrant further investigation.
+It's crucial to assess the model's assumptions, such as linearity, homoscedasticity, and normality of residuals, to ensure the validity of the statistical inferences made from the model.
+Understanding the reasons behind significant deviations can help improve the model and provide more accurate predictions.
+
+\newpage
 
 ### Plot for the linear model
-```{r echo=FALSE, warning=FALSE, message=FALSE}
+```{r fig-linear-plot, echo=FALSE, warning=FALSE, message=FALSE, fig.cap="plot for the linear relationship between building age and evaluation score"}
 # Create a scatter plot with a regression line to visualize the relationship
 improved_plot <- ggplot(cleaned_data, aes(x = AGE, y = CURRENT.BUILDING.EVAL.SCORE)) +
-  geom_point(alpha = 0.5, size = 1.5) +  # Adjust transparency and size of points
+  geom_point(alpha = 0.7, size = 1) +  # Adjust transparency and size of points
   geom_smooth(method = "lm", color = "blue", size = 1) +  # Change the size of the regression line
   labs(
-    x = "Age of Building",
+    x = "Building Age",
     y = "Current Building Evaluation Score",
-    title = "Relationship between Building Age and Evaluation Score"
   ) +
@@
   theme(
-    plot.title = element_text(face = "bold", hjust = 0.5, size = 16),
-    axis.title = element_text(size = 14),
-    axis.text = element_text(size = 12),
-    legend.position = "none"  # Hide the legend if not necessary
-  )
+    axis.text.x = element_text(angle = 45, hjust = 1, size = 8), # Rotate x axis text and adjust horizontal justification
+    axis.text.y = element_text(size = 8),
+    legend.position = "none", # Hide the legend if not necessary
+    plot.margin = margin(1, 1, 1, 1, "cm") # Adjust the margin around the plot
+  ) +
+  theme(legend.position = "bottom") # Move the legend to the bottom to prevent it from overlapping the plot
 
@@
 
-The graph provided illustrates the findings of a simple linear regression analysis that seeks to clarify the influence of one independent variable, building age, on the dependent variable, the building evaluation score.
-The scatterplot displays individual data points representing apartments, with the age of the building on the x-axis and the current building evaluation score on the y-axis.
+@fig-linear-plot provides a clear visual relationship between the age of buildings and their evaluation scores.
+Displayed with building age on the x-axis and evaluation score on the y-axis, the data points represent individual apartment buildings.
+The blue line running through the cluster of points represents the linear regression line, which captures the average effect of age on evaluation score.
+Noticeably, the slope of the line is downward, suggesting a negative correlation; as the buildings get older, their evaluation scores tend to decrease.
+This trend is consistent across the dataset, indicating a general decline in scores as building age increases, a reflection of the typical effects of wear and time on building integrity.
 
-A linear regression line has been fitted through the data, represented by the solid blue line, which indicates the average trend in the data.
-The slope of this line is a graphical representation of the regression coefficient associated with building age.
-In statistical terms, the slope tells us the average change in the evaluation score for each year increase in building age.
-If the slope is negative, it would suggest that, on average, older buildings tend to have lower evaluation scores.
-The density of the data points is heaviest near the younger age of buildings, and as age increases, the data points disperse more.
-This could suggest that there is greater variability in the scores of older buildings or that there are simply fewer older buildings in the dataset.
-
-Statistical significance is often determined by looking at the p-value for the slope of the regression line.
-In previous discussions, a p-value well below the threshold of 0.05 was mentioned, indicating that the effect of building age on evaluation score is indeed statistically significant.
-This would mean that there is a very low probability that the observed relationship, or one more extreme, would occur if there were actually no relationship between building age and evaluation score in the population.
-
-It is also important to examine the residuals, or the differences between the observed scores and those predicted by the model, which should be randomly dispersed without pattern if the model's assumptions hold true.
-In addition, the graph should be assessed for homoscedasticity, meaning that the variance of the residuals is constant across all levels of the independent variable.
-If the residuals fan out or form a funnel shape as building age increases, this would indicate heteroscedasticity, a violation of one of the linear regression assumptions, which could affect the reliability of the model.
-
-To summarize, this graph presents a visual and statistical summary of the relationship between building age and evaluation score, with the analysis revealing that age is a significant predictor of evaluation score, though it accounts for a relatively small portion of the variability in scores.
-Further analysis would be necessary to better understand the dispersion of scores, especially among older buildings, and to examine the model's underlying assumptions.
+In statistical analysis, the significance of this downward trend is supported by a p-value much lower than the conventional threshold of 0.05, confirming the relationship between building age and evaluation score is not due to random chance.
+However, the plot also reveals that while younger buildings cluster more densely around higher evaluation scores, older buildings exhibit a wider spread of scores.
+This variation suggests that other factors may influence the condition and safety of older buildings, which are not captured solely by age.
+The plot does not show any clear pattern or funnel shape in the residuals, indicating that the variance of the evaluation scores is fairly consistent across the range of building ages, and the assumption of homoscedasticity is not visibly violated.
+Nonetheless, the model's findings imply the importance of consistent maintenance and updates to older buildings to ensure safety standards are upheld over time.
 
@@
 
+## Appendix
+
 ## References

### 2024-03-13 scripts/01_download_data.R

@@ -1,9 +1,19 @@
-# Load necessary packages
+#### Preamble ####
+# Purpose: To download and preprocess the dataset related to building evaluation from the Toronto Open Data portal
+# Author: Terry Tu, Jingyi Shen, Yaning Jin
+# Date: 14 March 2024
+# Contact: xiangyu.tu@mail.utoronto.ca
+# License: MIT
+# Pre-requisites: The 'opendatatoronto' package for accessing open data, 'readr' and 'dplyr' for data manipulation, and 'here' for path management
+# Any other information needed? Ensure that the 'opendatatoronto' package is installed and updated to the latest version
+
+#### Workspace setup ####
 library(opendatatoronto)
 library(readr)
 library(dplyr)
 library(here)
 
+#### Data retrieval ####
 # Search for packages related to "building evaluation"
 search_result <- search_packages("building evaluation")
 
@@ -21,8 +31,12 @@ resource_id <- resources$id[1]
 # Download the resource
 building_evaluation_data <- get_resource(resource_id)
 
+#### Data preprocessing ####
+# Additional preprocessing steps would go here (if necessary)
+
+#### Save data ####
 # Save the data to a CSV file in the 'inputs/data' directory
-write_csv(building_evaluation_data, here("inputs", "data", "building_evaluation_data.csv"))
+write_csv(building_evaluation_data, here("data", "raw_data", "building_evaluation_data.csv"))
 
 # Print a message indicating completion
-cat("Data has been downloaded and saved as 'building_evaluation_data.csv' in the 'inputs/data' directory")
+cat("Data has been downloaded and saved as 'building_evaluation_data.csv' in the 'data/raw_data' directory")

### 2024-03-13 scripts/02_cleanup-data.R

@@ -1,16 +1,29 @@
-# Load necessary packages
+#### Preamble ####
+# Purpose: To clean the building evaluation data by removing NA values and calculating the AGE of buildings
+# Author: Terry Tu, Jingyi Shen, Yaning Jin
+# Date: 14 March 2024
+# Contact: xiangyu.tu@mail.utoronto.ca
+# License: MIT
+# Pre-requisites: 'readr' for reading CSV data, 'dplyr' for data manipulation, and 'here' for managing file paths
+# Any other information needed? The raw dataset must be located in the 'data/raw_data' directory before running this script
+
+#### Workspace setup ####
 library(readr)
 library(dplyr)
 library(here)
 
-# Load your existing data file into a data frame
-data <- read_csv(here("inputs", "data", "building_evaluation_data.csv"))
+#### Data cleaning ####
+# Load the raw data file into a data frame
+data <- read_csv(here("data", "raw_data", "building_evaluation_data.csv"))
 
-# Clean up the data by filtering out NAs in YEAR.BUILT and YEAR.EVALUATED
-# and then adding the 'AGE' column
+# Clean up the data by filtering out NAs in YEAR.BUILT and YEAR.EVALUATED and adding the 'AGE' column
 cleaned_data <- data %>%
   filter(!is.na(YEAR.BUILT) & !is.na(YEAR.EVALUATED)) %>%
   mutate(AGE = YEAR.EVALUATED - YEAR.BUILT)
 
+#### Save cleaned data ####
 # Save the cleaned data to a CSV file in the 'outputs/data' directory
-write_csv(cleaned_data, here("outputs", "data", "cleaned_building_data.csv"))
+write_csv(cleaned_data, here("data", "analysis_data", "cleaned_building_data.csv"))
+
+# Print a message indicating completion
+cat("Cleaned data has been saved as 'cleaned_building_data.csv' in the 'data/analysis_data' directory")

### 2024-03-13 scripts/03_test-data-validity.R

@@ -1,11 +1,21 @@
-# Load necessary packages
+#### Preamble ####
+# Purpose: To perform a series of data integrity tests on the cleaned building evaluation dataset
+# Author: Terry Tu, Jingyi Shen, Yaning Jin
+# Date: 14 March 2024
+# Contact: xiangyu.tu@mail.utoronto.ca
+# License: MIT
+# Pre-requisites: 'readr' for reading CSV data, 'dplyr' for data manipulation, 'here' for file path management, and 'testthat' for testing data integrity
+# Any other information needed? The cleaned dataset should be located in the 'data/analysis_data' directory and be free of processing errors
+
+#### Workspace setup ####
 library(readr)
 library(dplyr)
 library(here)
 library(testthat)
 
+#### Load and test data ####
 # Load the cleaned data file into a data frame
-data <- read_csv(here("outputs", "data", "cleaned_building_data.csv"))
+data <- read_csv(here("data", "analysis_data", "cleaned_building_data.csv"))
 
 # Define a function to perform the tests
 perform_data_tests <- function(data) {
@@ -28,4 +38,4 @@ perform_data_tests <- function(data) {
 }
 
 # Run the tests on the data
-perform_data_tests(data)
+test_results <- testthat::test_dir("tests")

### 2024-03-13 scripts/04_model.R

@@ -1,0 +1,28 @@
+#### Preamble ####
+# Purpose: To construct a linear model assessing the impact of building age on safety evaluation scores
+# Author: Terry Tu, Jingyi Shen, Yaning Jin
+# Date: 14 March 2024
+# Contact: xiangyu.tu@mail.utoronto.ca
+# License: MIT
+# Pre-requisites: The 'tidyverse' package for data manipulation and the 'here' package for path management
+# Any other information needed? Ensure that 'cleaned_data' has been appropriately pre-processed
+
+#### Workspace setup ####
+library(tidyverse)
+library(here)
+
+#### Read data ####
+cleaned_data <- read_csv(here("data", "analysis_data", "cleaned_building_data.csv"))
+
+### Model data ####
+lm_model <- lm(CURRENT.BUILDING.EVAL.SCORE ~ AGE, data = cleaned_data)
+
+# Summary of the model to check for immediate red flags
+summary(lm_model)
+
+#### Save model ####
+# Save the model as an .rds file to the 'models' folder
+saveRDS(
+  lm_model,
+  file = here("models", "linear_model.rds")
+)

### 2024-03-13 paper/paper.qmd
updated title

@@
 ---
-title: "Building Integrity in Retrospect: Assessing the Impact of Age on 2023 Safety Evaluations"
+title: "Structural Insights 2023: A Linear Analysis of Apartment Age and Safety Scores in Toronto"
 title-block-banner: true

### 2024-03-14 paper/paper.qmd
updated data and model

@@
 library(readr)
+library(knitr)
+library(kableExtra)
 ```
 
-## Introduction
+# Introduction
 
@@
 
-## Data
+# Data
 
@@
 ```
+
+## Raw Data
 
@@
 
-### Variable Description
+## Data Analysis Tools
+
+The data analysis was performed using R [@r], a powerful open-source statistical programming language.
+Key packages from the tidyverse collection [@rTidyverse] were employed to streamline data manipulation, visualization, and analysis processes.
+These packages include ggplot2 [@rGgplot2] for creating advanced graphics, dplyr [@rDplyr] for data manipulation, readr [@rReadr] for its robust data reading functionality, here [@R-here] is used to avoid file path issue, and knitr [@rKnitr] for dynamic report generation.
+
+## Variable Description
 
@@
 
-### Data Analysis Tools
+## Sample of Cleaned Building Evaluation Data
 
-The data analysis was performed using R [@r], a powerful open-source statistical programming language.
-Key packages from the tidyverse collection [@rTidyverse] were employed to streamline data manipulation, visualization, and analysis processes.
-These packages include ggplot2 [@rGgplot2] for creating advanced graphics, dplyr [@rDplyr] for data manipulation, readr [@rReadr] for its robust data reading functionality, here [@R-here] is used to avoid file path issue, and knitr [@rKnitr] for dynamic report generation.
+```{r}
+#| label: tbl-data-sample
+#| tbl-cap: Sample of Building Evaluation Data
+#| echo: false
+#| 
+# Select the first few rows of the dataset and the specific columns
+sample_data <- head(cleaned_data) %>%
+  select(X_id, AGE, CURRENT.BUILDING.EVAL.SCORE)
 
-### Data Exportation
+# Create a nicely formatted table
+kable(sample_data)
+```
+@tbl-data-sample represents a subset of the larger building evaluation data.
+Each row corresponds to a unique building identified by X_id.
+The AGE column indicates the age of the building in years, while the CURRENT.BUILDING.EVAL.SCORE column shows the building's current evaluation score on a scale from 0 to 100, with higher scores indicating better compliance with safety standards.
 
-After cleaning, the modified dataset, now stored in the `cleaned_data` data frame, is written to a new CSV file named 'cleaned_building_data.csv'.
-This file is saved in the 'outputs/data' directory, which is again constructed using the `here` function for path management.
-Saving the cleaned dataset allows for a stable version of the dataset to be used for analysis or sharing, ensuring reproducibility of results.
+## Data Exploration:
 
-Statistically, this script is preparing the dataset for analysis by ensuring the integrity and relevance of the data, which is foundational for any reliable statistical analysis.
-By creating the 'AGE' column, the script enables researchers to analyze the relationship between the age of a building and other variables of interest, such as compliance with property standards, in a quantitative manner.
+### Data Summary
+```{r}
+#| label: tbl-summary-table
+#| tbl-cap: Summary Statistics for the Cleaned Dataset
+#| echo: false
 
-## Model
+summary_data <- cleaned_data %>%
+  summarise(
+    Count = n(),
+    Mean_Age = mean(AGE, na.rm = TRUE),
+    Std_Age = sd(AGE, na.rm = TRUE),
+    Mean_Score = mean(CURRENT.BUILDING.EVAL.SCORE, na.rm = TRUE),
+    Std_Score = sd(CURRENT.BUILDING.EVAL.SCORE, na.rm = TRUE)
+  ) %>%
+  mutate(across(everything(), ~round(., 3)))
+
+# Create and print a nicely formatted table
+summary_table <- kable(summary_data, 
+                       col.names = c("Count", "Mean Age", "SD of Age", 
+                                     "Mean Score", "SD of Score"), 
+                       align = 'c') %>%
+  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), 
+                full_width = F, 
+                position = "center") %>%
+  column_spec(1, bold = TRUE) # Make the first column bold
+
+# Print the summary table
+summary_table
+```
+
+@tbl-summary-table presents a concise overview of the key descriptive metrics for the age of buildings and their evaluation scores within the dataset:
+
+- **Count**: The dataset encompasses a total of 1,748 buildings, indicating a robust sample size for statistical analysis.
+
+- **Mean Age**: The average age of the buildings is approximately 60.6 years, suggesting that the dataset primarily includes buildings that have been standing for over half a century.
+
+- **Standard Deviation of Age**: With a standard deviation of about 19.9 years, there is considerable variability in the ages of the buildings.
+This range implies a diverse sample, encompassing both relatively new constructions and much older structures.
+
+- **Mean Score**: The average building evaluation score is approximately 87.5 on a scale from 0 to 100.
+A higher score corresponds to better adherence to safety and maintenance standards, suggesting that the buildings in this dataset are generally well-maintained.
+
+- **Standard Deviation of Score**: The standard deviation of approximately 8.7 for the evaluation scores indicates that while scores are clustered around a high mean, there is still notable variability, reflecting differences in the condition or compliance of the buildings.
+
+These statistics offer a snapshot of the dataset's characteristics, providing foundational insights for further analysis regarding the state of building safety and integrity in the population studied.
+
+\newpage
+
+### Age Distribution
+```{r fig-age-distribution, echo=FALSE, fig.cap="Distribution of building's age for the cleaned data set"}
+# Histogram for the distribution of building age
+ggplot(cleaned_data, aes(x = AGE)) +
+  geom_histogram(binwidth = 5, fill = "steelblue", color = "white") +
+  labs(
+    x = "Age of Building (Years)",
+    y = "Frequency"
+  ) +
+  theme_minimal() +
+  theme(
+    plot.title = element_text(size = 16, face = "bold"),
+    axis.title = element_text(size = 14),
+    axis.text = element_text(size = 12)
+  )
+```
+
+@fig-age-distribution illustrates the frequency distribution of the ages of buildings within the dataset.
+The x-axis represents the age of the buildings in years, while the y-axis shows the frequency of buildings within each age range.
+The distribution appears to be unimodal with a peak around the 50-year mark, indicating that a substantial number of the buildings within this dataset were constructed around half a century ago.
+Following this peak, the frequency gradually decreases, showing that fewer buildings have been in existence beyond this age.
+The distribution suggests a relatively young building population, with ages concentrated below 100 years, and very few buildings reaching beyond 120 years of age.
+This visualization aids in understanding the age profile of buildings under consideration for safety evaluation scoring.
+
+\newpage
+
+### Score Distribution
+
+```{r fig-score-distribution, echo=FALSE, fig.cap="Distribution of building's evaluation score for the cleaned data set"}
+# Histogram for CURRENT.BUILDING.EVAL.SCORE distribution
+ggplot(cleaned_data, aes(x = CURRENT.BUILDING.EVAL.SCORE)) +
+  geom_histogram(binwidth = 5, fill = "darkgreen", color = "white") +
+  labs(
+    x = "Current Building Evaluation Score",
+    y = "Frequency"
+  ) +
+  theme_minimal() +
+  theme(
+    plot.title = element_text(size = 16, face = "bold"),
+    axis.title = element_text(size = 14),
+    axis.text = element_text(size = 12)
+  )
+```
+
+@fig-score-distribution showcases the distribution of building evaluation scores.
+The x-axis represents the scores assigned to buildings, which can range from 0 to 100, with the y-axis displaying the frequency of buildings for each score interval.
+The chart reveals a concentration of high evaluation scores, suggesting that many of the buildings in the dataset are rated as being in good or excellent condition according to the evaluation criteria.
+The tallest bars are clustered towards the higher end of the score range, indicating that buildings with scores close to 100 are prevalent.
+This positive skew in the distribution might reflect effective building standards and maintenance practices in place.
+The spread of the scores and their frequency can offer insights into the overall health of the evaluated buildings, influencing urban planning and policy development.
+
+# Model
 
@@
 
-### Model set-up
+## Model set-up
 
@@
 y_i &\sim \mbox{Normal}(\mu_i, \sigma) \\
-\mu_i &= \beta_0 + \beta_1 \times \mbox{AGE}_i \\
+\mu_i &= \beta_0 + \beta_1 \times x_i \\
 \beta_0 &\sim \mbox{Normal}(90, 10) \\
@@
 
-The model is executed in R using the lm function. We select normal priors for the intercept and slope based on initial exploratory data analysis.
+The model is implemented in R using the rstanarm package, which allows us to incorporate prior beliefs about the parameters and to estimate the posterior distributions.
+For the intercept $\beta_0$ and slope $\beta_1$ , we choose normal prior distributions centered around our initial estimates based on exploratory data analysis.
+The `stan_glm` function from `rstanarm` is utilized to carry out the Bayesian regression, providing a framework for inference that incorporates both the data and our prior knowledge.
 
-### Model justification
+The priors are chosen to reflect reasonable beliefs about the parameters before observing the data.
+The intercept prior reflects an expectation that a new building will have a high safety score around 90, with a wide spread to accommodate uncertainty.
+Similarly, the slope prior indicates an expected small negative impact of age on the safety score, acknowledging some uncertainty in the precise effect.
+The `stan_glm` function combines these priors with the data to estimate the posterior distributions of the model parameters.
 
-A negative coefficient for AGE is anticipated, hypothesizing that older buildings may have lower safety scores due to factors such as wear and deterioration over time.
-We anticipate the intercept to represent the evaluation score for a newly built property, with the slope capturing the average yearly decrease in score.
+## Model justification
 
-## Result
+We hypothesize that the coefficient for building age ($\beta_1$) will be negative, reflecting the tendency for older buildings to exhibit lower safety scores.
+This expectation is rooted in the general understanding that buildings can deteriorate over time due to wear, aging materials, and possible obsolescence in older construction methods.
+The intercept ($\beta_0$), representing the baseline evaluation score for a new building, is presumed to be relatively high, indicating the score a building would receive if it were built in the current period with modern standards.
+The slope ($\beta_1$) is therefore of particular interest, as it encapsulates the average annual decline in evaluation score attributable to aging.
+The Bayesian framework allows us to incorporate these hypotheses as priors in our model, thereby aligning the analysis with our substantive expectations and providing a more nuanced interpretation of the data.
+
+# Result
 
 ```{r echo=FALSE}
-# Retrieve the linear model from the saved .rds file
-lm_model <- readRDS(file = here("models", "linear_model.rds"))
+# Retrieve the Bayesian linear model from the saved .rds file
+bayesian_model <- readRDS(file = here("models", "bayesian_linear_model.rds"))
 ```
 
-### Model Coefficients Interpretation
+## Model Coefficients Interpretation
 
 ```{r echo=FALSE}
-# Extract coefficients from the model
-coefficients <- summary(lm_model)$coefficients
-coefficients
+# Extract coefficients from the Bayesian model
+coefficients <- coef(bayesian_model)
+print(coefficients)
 ```
@@
 
-**Intercept** ($\beta_0$)  
-The model estimates the intercept, $\beta_0$, to be 93.61663.
-This is the predicted evaluation score for a building at the time it is newly constructed, where AGE equals zero.
-Accompanied by a standard error of 0.64805, this coefficient's estimate signals the level of precision with which we can predict the evaluation score for new buildings.
-The t-value associated with the intercept is 144.459, which is highly significant, as indicated by the p-value of practically zero.
-This signifies a very strong statistical assurance in the intercept's estimate.
+**Intercept** ($\beta_0$):  
+The model's intercept, $\beta_0$, with a mean posterior estimate of 93.55985, represents the baseline evaluation score for a hypothetical newly constructed building.
+In Bayesian terms, this value is not a single point estimate but rather the mean of the posterior distribution for the intercept.
+This distribution reflects our belief about the probable values of the evaluation score for a new building, informed by the data and our prior assumptions.
 
-**Slope** ($\beta_1$)  
-The slope of the model, $\beta_1$, is determined to be -0.10079.
-This value quantifies the expected change in the building evaluation score for each additional year of age; specifically, the score is projected to decrease by about 0.10079 points annually.
-The standard error of 0.01015 suggests high precision in this estimation.
-The t-value of -9.929 reaffirms the reliability of this coefficient, with a corresponding p-value of 1.226807e-22, far below the 0.05 threshold, confirming the impact of age on evaluation scores is statistically significant.
+**Slope** ($\beta_1$):  
+Similarly, the slope parameter $\beta_1$ has a mean posterior estimate of -0.10059.
+It describes the average decrease in the evaluation score associated with each additional year of a building's age.
+Again, this is the mean of the posterior distribution for the slope, encompassing both our prior beliefs and the observed data.
+A mean estimate that is negative suggests a trend where older buildings have lower evaluation scores.
 
-These coefficients paint a picture of gradual decline in building quality as measured by the evaluation scores over time.
-The statistical significance of both coefficients assures us that the model's predictions are based on real effects and not on random fluctuations within the dataset.
-This analysis emphasizes the need for rigorous maintenance and periodic updates to older buildings to preserve their integrity and safety.
+**Interpretation**:
+The Bayesian analysis suggests that there is a likely negative relationship between building age and evaluation score.
+The mean estimates of the intercept and slope, along with their posterior distributions, indicate that newer buildings tend to have higher evaluation scores, which decrease as buildings age.
+This trend highlights the importance of age as a factor in building evaluations and underscores the need for ongoing maintenance and updates to preserve building safety and integrity over time.
 
-### Model Equation
+## Model Equation
 
@@
 y_i &\sim \mbox{Normal}(\mu_i, \sigma) \\
-\mu_i &= \beta_0 + \beta_1 \times \mbox{AGE}_i \\
-\beta_0 &= 93.6166 \\
-\beta_1 &= -0.1008
+\mu_i &= \beta_0 + \beta_1 \times x_i \\
+\beta_0 &= 93.55985 \\
+\beta_1 &= -0.10059
 \end{align}
 
-In this model, $y_i$ represents the predicted evaluation score for the $i$-th building, $\mu_i$ is the mean of the normal distribution for the $i$-th observation, $\beta_0$ is the intercept, and $\beta_1$ is the slope representing the change in evaluation score per year of building age.
+In this model, $y_i$ represents the predicted evaluation score for the $i$-th building, $x_i$ represents the age for the $i$-th building, $\mu_i$ is the mean of the normal distribution for the $i$-th observation, $\beta_0$ is the intercept, and $\beta_1$ is the slope representing the change in evaluation score per year of building age.
 
-### Analysis of Residuals
+## Analysis of Residuals
 
 ```{r echo=FALSE}
-# Extract residuals from the model
-residuals <- resid(lm_model)
+# Extract residuals from the Bayesian model
+residuals <- residuals(bayesian_model)
 summary(residuals)
@@
 **1.
-Minimum Residual**: The minimum residual is -69.662, indicating that there is at least one building for which the model's predicted evaluation score was lower than the actual score by approximately 69.662 points.
+Minimum Residual**: The minimum residual is approximately -69.619, indicating that there is at least one building for which the model's predicted evaluation score was lower than the actual score by approximately 69.662 points.
 This could be an outlier or a building with exceptional characteristics not captured by the model.
@@
 **2.
-First Quartile Residual**: The first quartile (Q1) of the residuals is -4.364, meaning that 25% of the buildings have evaluation scores that are less than 4.364 points below the model's prediction for their age.
+First Quartile Residual**: The first quartile (Q1) of the residuals is approximately -4.320, meaning that 25% of the buildings have evaluation scores that are less than 4.364 points below the model's prediction for their age.
 
 **3.
-Median Residual**: The median residual is 1.702, suggesting a slight positive bias in the model's predictions, as the median of the error distribution is above zero.
+Median Residual**: The median residual is approximately 1.757, suggesting a slight positive bias in the model's predictions, as the median of the error distribution is above zero.
 This indicates that, on average, the model tends to slightly overestimate the evaluation scores.
@@
 **4.
-Third Quartile Residual**: The third quartile (Q3) is 5.833, indicating that 75% of the buildings have evaluation scores within 5.833 points of the model's predictions or better.
+Third Quartile Residual**: The third quartile (Q3) is approximately 5.878, indicating that 75% of the buildings have evaluation scores within 5.833 points of the model's predictions or better.
 This shows that the model provides reasonably accurate predictions for the majority of buildings.
@@
 **5.
-Maximum Residual**: The maximum residual is 15.859, suggesting that there is at least one building for which the model's predicted evaluation score was higher than the actual score by approximately 15.859 points.
+Maximum Residual**: The maximum residual is approximately 15.896, suggesting that there is at least one building for which the model's predicted evaluation score was higher than the actual score by approximately 15.896 points.
 This could be another outlier or a building that performed exceptionally well.
@@
 
-### Plot for the linear model
+## Plot for the linear model
 ```{r fig-linear-plot, echo=FALSE, warning=FALSE, message=FALSE, fig.cap="plot for the linear relationship between building age and evaluation score"}
-# Create a scatter plot with a regression line to visualize the relationship
+# Enhanced scatter plot with regression line
 improved_plot <- ggplot(cleaned_data, aes(x = AGE, y = CURRENT.BUILDING.EVAL.SCORE)) +
   geom_point(alpha = 0.7, size = 1) +  # Adjust transparency and size of points
-  geom_smooth(method = "lm", color = "blue", size = 1) +  # Change the size of the regression line
+  geom_smooth(method = "lm", color = "blue", size = 1) +  
   labs(
     x = "Building Age",
-    y = "Current Building Evaluation Score",
+    y = "Building Evaluation Score",
+    title = "Impact of Building Age on Evaluation Score"
   ) +
@@
   theme(
-    axis.text.x = element_text(angle = 45, hjust = 1, size = 8), # Rotate x axis text and adjust horizontal justification
-    axis.text.y = element_text(size = 8),
-    legend.position = "none", # Hide the legend if not necessary
-    plot.margin = margin(1, 1, 1, 1, "cm") # Adjust the margin around the plot
-  ) +
-  theme(legend.position = "bottom") # Move the legend to the bottom to prevent it from overlapping the plot
+    plot.title = element_text(size = 14),
+    axis.title.x = element_text(size = 12),
+    axis.title.y = element_text(size = 12),
+    axis.text.x = element_text(angle = 45, hjust = 1),
+    axis.text.y = element_text(size = 10),
+    legend.position = "none"  # Hide the legend if not necessary
+  )
 
-# Print the improved plot
+# Display the plot
 print(improved_plot)
@@
 
-## Discussion
+# Discussion
 
-### Overview of the Study
+## Overview of the Study
 
@@
 
-### Insights into Urban Development and Maintenance
+## Insights into Urban Development and Maintenance
 
@@
 
-### Policy Implications and Housing Quality
+## Policy Implications and Housing Quality
 
@@
 
-### Limitations of the Study
+## Limitations of the Study
 
@@
 
-### Future Directions
+## Future Directions
 
@@
 
-## Appendix
+# Appendix
 
-## References
+# References

### 2024-03-14 scripts/01_download_data.R

@@ -5,7 +5,7 @@
 # Contact: xiangyu.tu@mail.utoronto.ca
 # License: MIT
 # Pre-requisites: The 'opendatatoronto' package for accessing open data, 'readr' and 'dplyr' for data manipulation, and 'here' for path management
-# Any other information needed? Ensure that the 'opendatatoronto' package is installed and updated to the latest version
+# Ensure that the 'opendatatoronto' package is installed and updated to the latest version
 
 #### Workspace setup ####
 library(opendatatoronto)

### 2024-03-14 scripts/02_cleanup-data.R

@@ -5,7 +5,7 @@
 # Contact: xiangyu.tu@mail.utoronto.ca
 # License: MIT
 # Pre-requisites: 'readr' for reading CSV data, 'dplyr' for data manipulation, and 'here' for managing file paths
-# Any other information needed? The raw dataset must be located in the 'data/raw_data' directory before running this script
+# The raw dataset must be located in the 'data/raw_data' directory before running this script
 
 #### Workspace setup ####
 library(readr)

### 2024-03-14 scripts/03_test-data-validity.R

@@ -4,38 +4,32 @@
 # Date: 14 March 2024
 # Contact: xiangyu.tu@mail.utoronto.ca
 # License: MIT
-# Pre-requisites: 'readr' for reading CSV data, 'dplyr' for data manipulation, 'here' for file path management, and 'testthat' for testing data integrity
-# Any other information needed? The cleaned dataset should be located in the 'data/analysis_data' directory and be free of processing errors
+# Pre-requisites: 'readr' for reading CSV data, 'dplyr' for data manipulation, 'here' for file path management
+# The cleaned dataset should be located in the 'data/analysis_data' directory and be free of processing errors
 
 #### Workspace setup ####
 library(readr)
 library(dplyr)
 library(here)
-library(testthat)
 
-#### Load and test data ####
-# Load the cleaned data file into a data frame
-data <- read_csv(here("data", "analysis_data", "cleaned_building_data.csv"))
+# Load the cleaned data file into a variable 'data'
+file_path <- here("data", "analysis_data", "cleaned_building_data.csv")
+data <- read_csv(file_path)
 
-# Define a function to perform the tests
-perform_data_tests <- function(data) {
-  # Test if AGE column has no negative values
-  test_that("AGE column contains no negative values", {
-    expect_true(all(data$AGE >= 0), info = "There are negative values in the AGE column")
-  })
-  
-  # Test if YEAR.BUILT, YEAR.EVALUATED, CURRENT.BUILDING.EVAL.SCORE have no NA values
-  test_that("No NA values in YEAR.BUILT, YEAR.EVALUATED, CURRENT.BUILDING.EVAL.SCORE", {
-    expect_true(all(!is.na(data$YEAR.BUILT)), info = "There are NA values in YEAR.BUILT")
-    expect_true(all(!is.na(data$YEAR.EVALUATED)), info = "There are NA values in YEAR.EVALUATED")
-    expect_true(all(!is.na(data$CURRENT.BUILDING.EVAL.SCORE)), info = "There are NA values in CURRENT.BUILDING.EVAL.SCORE")
-  })
-  
-  # Test if CURRENT.BUILDING.EVAL.SCORE column has no negative values
-  test_that("CURRENT.BUILDING.EVAL.SCORE column contains no negative values", {
[…]

### 2024-03-14 scripts/04_model.R

@@ -1,28 +1,39 @@
 #### Preamble ####
-# Purpose: To construct a linear model assessing the impact of building age on safety evaluation scores
+# Purpose: To construct a Bayesian linear model assessing the impact of building age on safety evaluation scores using rstanarm
 # Author: Terry Tu, Jingyi Shen, Yaning Jin
 # Date: 14 March 2024
 # Contact: xiangyu.tu@mail.utoronto.ca
 # License: MIT
-# Pre-requisites: The 'tidyverse' package for data manipulation and the 'here' package for path management
-# Any other information needed? Ensure that 'cleaned_data' has been appropriately pre-processed
+# Pre-requisites: The 'rstanarm' package for Bayesian modeling, 'readr' for data manipulation, and 'here' for path management
+# The 'cleaned_data' dataset must be pre-processed before using it in the model.
 
 #### Workspace setup ####
-library(tidyverse)
+library(readr)
+library(rstanarm)
 library(here)
 
 #### Read data ####
 cleaned_data <- read_csv(here("data", "analysis_data", "cleaned_building_data.csv"))
 
+# Ensure reproducibility
+set.seed(2024)
+
 ### Model data ####
-lm_model <- lm(CURRENT.BUILDING.EVAL.SCORE ~ AGE, data = cleaned_data)
+bayesian_model <- stan_glm(
+  CURRENT.BUILDING.EVAL.SCORE ~ AGE, 
+  data = cleaned_data,
+  family = gaussian(), # Assuming a normal distribution for the response variable
+  prior = normal(0, 2.5, autoscale = FALSE), # Set the prior for the coefficients
+  prior_intercept = normal(0, 10, autoscale = FALSE), # Set the prior for the intercept
+  seed = 2024 # Set the seed for reproducibility
+)
 
 # Summary of the model to check for immediate red flags
-summary(lm_model)
+summary(bayesian_model)
 
 #### Save model ####
-# Save the model as an .rds file to the 'models' folder
+# Save the Bayesian model as an .rds file to the 'models' folder
 saveRDS(
-  lm_model,
-  file = here("models", "linear_model.rds")
+  bayesian_model,
+  file = here("models", "bayesian_linear_model.rds")
 )

### 2024-03-15 paper/paper.qmd
revised new model, intro, results

@@
 
-In the wake of the catastrophic collapse of an aged condominium in South Florida in June 2021, which resulted in 98 casualties, a subsequent lawsuit by the bereaved families underscored the notion that routine inspections and maintenance could have forestalled the disaster[@Anderson_2021].
-This incident precipitates our investigation into forecasting the building evaluation scores for Toronto residences in 2023 via a simple linear regression model.
-An analysis was conducted on the apartment building evaluation dataset obtained from the City of Toronto's open data portal to assess the relationship between the age of a property and its evaluation score assigned by the city.
-Our research is singularly focused on elucidating the effect of one independent variable—building age—on the dependent variable, which in this context is the building evaluation score.
+The structural integrity of urban buildings is a paramount concern for city planners, policymakers, and residents alike.
+The tragic collapse of a condominium in South Florida in June 2021, which resulted in 98 casualties, serves as a stark reminder of the potential consequences of neglecting building maintenance and inspections [@Anderson_2021].
+This event highlights a critical gap in our understanding of the factors that contribute to the safety and longevity of urban residential structures.
+In light of this, our study aims to investigate the relationship between building age and evaluation scores in the context of Toronto's residential buildings.
 
-Using simple linear regression analysis enables a detailed exploration of the linear relationship between the age of a building and its evaluation score.
-By quantifying this relationship through regression coefficients, we aim to reveal the expected change in evaluation scores for each incremental year in building age.
-The statistical significance of the age variable on evaluation scores will be ascertained using p-values.
-Provided the model satisfies the underlying assumptions, t-tests will be applied to test the hypotheses, while confidence and prediction intervals will be leveraged to quantify the effect size and enhance the accuracy of our forecasts, respectively.
+Our study's estimand is the effect of building age on evaluation scores in Toronto.
+We investigate how the age of buildings influences their assigned evaluation scores, reflecting their compliance with safety standards and overall condition.
+Utilizing a dataset from the Toronto Open Data portal, which includes 3,435 records, we apply a simple linear regression model to forecast evaluation scores for Toronto residences in 2023.
+By conducting this analysis, we aim to quantify the impact of building age on evaluation scores and understand its implications for urban housing safety and maintenance.
 
-# Data
+The analysis reveals a statistically significant inverse relationship between building age and evaluation score, indicating that older buildings tend to receive lower evaluation scores.
+This finding highlights the critical need for regular inspections and maintenance to preserve the safety and habitability of aging buildings.
+It also suggests that policies should prioritize the maintenance and inspection of older structures to prevent potential safety hazards.
+
+Moreover, our study offers insights into urban development and maintenance, suggesting that policymakers might need to revisit regulations surrounding building inspections and maintenance schedules.
+It further emphasizes the importance of continuous monitoring and evaluation by urban authorities to maintain and enhance housing standards across the city.
+These insights carry substantial implications for urban planning and public safety, underscoring the necessity of proactive measures to mitigate risks associated with aging infrastructure.
+In conclusion, this paper significantly advances our understanding of the relationship between building age and evaluation scores, underlining the importance of proactive strategies to ensure the safety and integrity of the urban housing stock.
+
+The remainder of this paper is structured as follows: @sec-data (Data) details the raw data, the cleaning process, and provides an overview of the data distribution.
+@sec-model (Model) describes the linear model employed to predict the building evaluation score based on the building's age.
+@sec-result (Results) presents the coefficients of the linear model, analyses the residuals, and includes a plot illustrating the linear model applied to the analysis dataset.
+Finally, @sec-discussion (Discussion) discusses the limitations of the analysis and suggests potential insights for future research.
+
+# Data {#sec-data}
 
@@
 
-In this research, we examine apartment data sourced from the Toronto Open Data portal.
+In this research, we examine apartment data sourced using the `opendatatoronto` package [@Toronto_2023].
 The dataset encompasses 3,435 records, focusing on specific variables: the ward of each apartment, its evaluation score, and the construction year.
@@
 These apartments span a wide range of construction years, from as early as 1805 to as recent as 2023.
-All the apartments in this dataset adhere to the City's Apartment Building Standards bylaw, which is designed to safeguard the interests and safety of both landlords and tenants by mandating these evaluations [@Toronto_2023].
+All the apartments in this dataset adhere to the City's Apartment Building Standards bylaw, which is designed to safeguard the interests and safety of both landlords and tenants by mandating these evaluations.
 
@@
 The data analysis was performed using R [@r], a powerful open-source statistical programming language.
-Key packages from the tidyverse collection [@rTidyverse] were employed to streamline data manipulation, visualization, and analysis processes.
-These packages include ggplot2 [@rGgplot2] for creating advanced graphics, dplyr [@rDplyr] for data manipulation, readr [@rReadr] for its robust data reading functionality, here [@R-here] is used to avoid file path issue, and knitr [@rKnitr] for dynamic report generation.
+A suite of packages from the tidyverse [@rTidyverse], an assemblage of R packages designed for data science, was harnessed to enhance the efficiency of our data operations.
+The `ggplot2` package [@rGgplot2] facilitated the creation of sophisticated visualizations, while `dplyr` [@rDplyr] provided a grammar of data manipulation, offering a coherent set of verbs that help in filtering, summarizing, and arranging the dataset.
+The `readr` package [@rReadr] was utilized for its fast and friendly data reading capabilities.
+Navigation and file path management were streamlined using the `here` package [@R-here], simplifying the process of file referencing within the project's directory structure.
+Report generation was dynamically handled by knitr [@rKnitr], enabling the integration of R code within this document.
+Additionally, `kableExtra`[@R-kableExtra] was employed to produce aesthetically pleasing and customizable tables, enriching the presentation of our results.
+For the Bayesian analysis, rstanarm [@R-rstanarm] was utilized to create a linear model, providing an elegant interface to Stan, a state-of-the-art platform for statistical modeling and high-performance statistical computation.
+This package enabled us to estimate the relationship between building age and safety evaluation scores using a Bayesian framework.
 
@@
 #| echo: false
-#| 
-# Select the first few rows of the dataset and the specific columns
+
 sample_data <- head(cleaned_data) %>%
@@
 
-# Create a nicely formatted table
-kable(sample_data)
+# Create a nicely formatted table with custom column names
+kable(sample_data, col.names = c("Building ID", "Age (Years)", "Evaluation Score"))
 ```
@@
 summary_table <- kable(summary_data, 
-                       col.names = c("Count", "Mean Age", "SD of Age", 
+                       col.names = c("Count", "Mean Age (Years)", "SD of Age (Years)", 
                                      "Mean Score", "SD of Score"), 
@@
 
-- **Mean Age**: The average age of the buildings is approximately 60.6 years, suggesting that the dataset primarily includes buildings that have been standing for over half a century.
+- **Mean Age**: The average age of the buildings is approximately 60.644 years, suggesting that the dataset primarily includes buildings that have been standing for over half a century.
 
-- **Standard Deviation of Age**: With a standard deviation of about 19.9 years, there is considerable variability in the ages of the buildings.
+- **Standard Deviation of Age**: With a standard deviation of about 19.939 years, there is considerable variability in the ages of the buildings.
 This range implies a diverse sample, encompassing both relatively new constructions and much older structures.
 
-- **Mean Score**: The average building evaluation score is approximately 87.5 on a scale from 0 to 100.
+- **Mean Score**: The average building evaluation score is approximately 87.504 on a scale from 0 to 100.
 A higher score corresponds to better adherence to safety and maintenance standards, suggesting that the buildings in this dataset are generally well-maintained.
 
-- **Standard Deviation of Score**: The standard deviation of approximately 8.7 for the evaluation scores indicates that while scores are clustered around a high mean, there is still notable variability, reflecting differences in the condition or compliance of the buildings.
+- **Standard Deviation of Score**: The standard deviation of approximately 8.693 for the evaluation scores indicates that while scores are clustered around a high mean, there is still notable variability, reflecting differences in the condition or compliance of the buildings.
 
 These statistics offer a snapshot of the dataset's characteristics, providing foundational insights for further analysis regarding the state of building safety and integrity in the population studied.
-
-\newpage
 
@@
 This visualization aids in understanding the age profile of buildings under consideration for safety evaluation scoring.
-
-\newpage
 
@@
 
-# Model
+# Model {#sec-model}
 
@@
 \begin{align}
-y_i &\sim \mbox{Normal}(\mu_i, \sigma) \\
-\mu_i &= \beta_0 + \beta_1 \times x_i \\
-\beta_0 &\sim \mbox{Normal}(90, 10) \\
-\beta_1 &\sim \mbox{Normal}(-0.1, 0.05)
+y_i &\sim \mbox{Normal}(\mu_i, \sigma) \
+\mu_i &= \beta_0 + \beta_1 \times \mbox{AGE}_i \
+\beta_0 &\sim \mbox{Normal}(85, 10) \
+\beta_1 &\sim \mbox{Normal}(0, 0.05)
 \end{align}
@@
 
-# Result
+# Result {#sec-result}
 
@@
 
-```{r echo=FALSE}
+```{r}
+#| label: tbl-coefficient-table
+#| tbl-cap: Summary Statistics for the Coefficients of the Linear Model
+#| echo: false
+
 # Extract coefficients from the Bayesian model
 coefficients <- coef(bayesian_model)
-print(coefficients)
+
+# Convert coefficients to a data frame for better formatting
+coefficients_df <- data.frame(
+  Term = c("Intercept", "Slope"),
+  Estimate = unname(coefficients) 
+)
+
+# Round the estimates to three digits
+coefficients_df$Estimate <- round(coefficients_df$Estimate, 3)
+
+# Create a nicely formatted table
+coefficient_table <- kable(coefficients_df,
+                           col.names = c("Term", "Estimate"),
+                           align = 'c') %>%
+  kable_styling(bootstrap_options = c("striped", "hover", "condensed"),
+                full_width = FALSE,
+                position = "center")
+
+# Print the summary table
+coefficient_table
 ```
-The regression model provides two key coefficients to understand the relationship between building age and the evaluation score:
+
+@tbl-coefficient-table provides two key coefficients to understand the relationship between building age and the evaluation score:
 
 **Intercept** ($\beta_0$):  
-The model's intercept, $\beta_0$, with a mean posterior estimate of 93.55985, represents the baseline evaluation score for a hypothetical newly constructed building.
-In Bayesian terms, this value is not a single point estimate but rather the mean of the posterior distribution for the intercept.
-This distribution reflects our belief about the probable values of the evaluation score for a new building, informed by the data and our prior assumptions.
+The model's intercept, $\beta_0$, has an estimate of 93.364.
+This represents the baseline evaluation score for a hypothetical newly constructed building.
+The intercept suggests that if a building were constructed in the current year, its expected evaluation score would be around 93.364, assuming all other factors remain constant.
 
 **Slope** ($\beta_1$):  
-Similarly, the slope parameter $\beta_1$ has a mean posterior estimate of -0.10059.
-It describes the average decrease in the evaluation score associated with each additional year of a building's age.
-Again, this is the mean of the posterior distribution for the slope, encompassing both our prior beliefs and the observed data.
-A mean estimate that is negative suggests a trend where older buildings have lower evaluation scores.
+The slope parameter, $\beta_1$, has an estimate of -0.097.
+This indicates that, on average, the evaluation score is expected to decrease by approximately 0.097 points for each additional year of a building's age.
+This negative value suggests a trend where older buildings tend to have lower evaluation scores compared to newer ones.
 
 **Interpretation**:
-The Bayesian analysis suggests that there is a likely negative relationship between building age and evaluation score.
-The mean estimates of the intercept and slope, along with their posterior distributions, indicate that newer buildings tend to have higher evaluation scores, which decrease as buildings age.
+The analysis suggests a negative relationship between building age and evaluation score.
+The estimates indicate that newer buildings tend to have higher evaluation scores, which decrease as buildings age.
 This trend highlights the importance of age as a factor in building evaluations and underscores the need for ongoing maintenance and updates to preserve building safety and integrity over time.
@@
 \mu_i &= \beta_0 + \beta_1 \times x_i \\
-\beta_0 &= 93.55985 \\
-\beta_1 &= -0.10059
+\beta_0 &= 93.364 \\
+\beta_1 &= -0.097
 \end{align}
@@
 
-```{r echo=FALSE}
+```{r}
+#| label: tbl-residuals-summary
+#| tbl-cap: Summary Statistics for the Residuals of the Bayesian Linear Model
+#| echo: false
+
 # Extract residuals from the Bayesian model
 residuals <- residuals(bayesian_model)
-summary(residuals)
+
+# Create a summary table for residuals and round to three digits
+residuals_rounded <- round(summary(residuals), 3)
+
+# Create a data frame for better formatting
+residuals_summary_df <- data.frame(
+  Statistic = c("Min", "1st Qu.", "Median", "Mean", "3rd Qu.", "Max"),
+  Value = as.numeric(residuals_rounded)  # Convert to numeric to ensure proper formatting
+)
+
+# Create a nicely formatted table
+residuals_table <- kable(residuals_summary_df,
+                         col.names = c("Residual Statistics", "Value"),
+                         align = 'c')
+
+# Print the summary table
+residuals_table
 ```
@@
 **1.
-Minimum Residual**: The minimum residual is approximately -69.619, indicating that there is at least one building for which the model's predicted evaluation score was lower than the actual score by approximately 69.662 points.
+Minimum Residual**: The minimum residual is -69.700, indicating that there is at least one building for which the model's predicted evaluation score was lower than the actual score by approximately 69.700 points.
 This could be an outlier or a building with exceptional characteristics not captured by the model.
@@
 **2.
-First Quartile Residual**: The first quartile (Q1) of the residuals is approximately -4.320, meaning that 25% of the buildings have evaluation scores that are less than 4.364 points below the model's prediction for their age.
+First Quartile Residual**: The first quartile (Q1) of the residuals is -4.440, meaning that 25% of the buildings have evaluation scores that are less than 4.440 points below the model's prediction for their age.
 
 **3.
-Median Residual**: The median residual is approximately 1.757, suggesting a slight positive bias in the model's predictions, as the median of the error distribution is above zero.
+Median Residual**: The median residual is 1.687, suggesting a slight positive bias in the model's predictions, as the median of the error distribution is above zero.
 This indicates that, on average, the model tends to slightly overestimate the evaluation scores.
@@
 **4.
-Third Quartile Residual**: The third quartile (Q3) is approximately 5.878, indicating that 75% of the buildings have evaluation scores within 5.833 points of the model's predictions or better.
+Third Quartile Residual**: The third quartile (Q3) is 5.860, indicating that 75% of the buildings have evaluation scores within 5.860 points of the model's predictions or better.
 This shows that the model provides reasonably accurate predictions for the majority of buildings.
@@
 **5.
-Maximum Residual**: The maximum residual is approximately 15.896, suggesting that there is at least one building for which the model's predicted evaluation score was higher than the actual score by approximately 15.896 points.
+Maximum Residual**: The maximum residual is 15.715, suggesting that there is at least one building for which the model's predicted evaluation score was higher than the actual score by approximately 15.715 points.
 This could be another outlier or a building that performed exceptionally well.
@@
 
-# Discussion
+# Discussion {#sec-discussion}
 

### 2024-03-15 scripts/00_simulate-data.R

@@ -1,0 +1,44 @@
+#### Preamble ####
+# Purpose: Simulate a dataset with a negative relationship between building age and evaluation score
+# Author: Terry Tu, Jingyi Shen, Yaning Jin
+# Date: 14 March 2024
+# Contact: xiangyu.tu@mail.utoronto.ca
+# License: MIT
+# Pre-requisites: tidyverse package
+
+# Load necessary libraries
+library(tidyverse)
+
+# Set a seed for reproducibility
+set.seed(123)
+
+# Define the number of buildings to simulate
+n_buildings <- 1000
+
+# Generate building ages
+building_ages <- round(runif(n_buildings, min = 0, max = 120))
+
+# Define parameters for the linear relationship
+intercept <- 100  # Baseline score for a new building
+slope <- -0.5     # Negative slope indicating decrease in score with age
+
+# Generate evaluation scores with some random noise
+evaluation_scores <- intercept + slope * building_ages + rnorm(n_buildings, mean = 0, sd = 10)
+
+# Combine ages and scores into a data frame
+simulated_data <- tibble(
+  Building_Age = building_ages,
+  Evaluation_Score = evaluation_scores
+)
+
+# Inspect the first few rows of the simulated data
+head(simulated_data)
+
+# Plot the simulated data
+ggplot(simulated_data, aes(x = Building_Age, y = Evaluation_Score)) +
+  geom_point() +
+  geom_smooth(method = "lm", se = FALSE, color = "blue") +
+  labs(title = "Simulated Data: Building Age vs. Evaluation Score",
+       x = "Building Age (years)",
+       y = "Evaluation Score") +
+  theme_minimal()

### 2024-03-15 scripts/03_test-data-validity.R

@@ -28,8 +28,12 @@ test_no_na <- all(!is.na(data$YEAR.BUILT) & !is.na(data$YEAR.EVALUATED) & !is.na
 # Test 3: CURRENT.BUILDING.EVAL.SCORE values are within the range 0 to 100
 test_score_range <- all(data$CURRENT.BUILDING.EVAL.SCORE >= 0 & data$CURRENT.BUILDING.EVAL.SCORE <= 100)
 
+# Test 4: All YEAR.EVALUATED values are 2023
+test_year_evaluated <- all(data$YEAR.EVALUATED == 2023)
+
 # Print the result from the tests
 print(paste("Test 1 - No negative values in AGE:", test_age_positive))
 print(paste("Test 2 - No NA values in critical columns:", test_no_na))
 print(paste("Test 3 - Building scores are within the range of 0 to 100:", test_score_range))
+print(paste("Test 4 - All YEAR.EVALUATED values are 2023:", test_year_evaluated))
 

### 2024-03-15 scripts/04_model.R

@@ -23,8 +23,8 @@ bayesian_model <- stan_glm(
   CURRENT.BUILDING.EVAL.SCORE ~ AGE, 
   data = cleaned_data,
   family = gaussian(), # Assuming a normal distribution for the response variable
-  prior = normal(0, 2.5, autoscale = FALSE), # Set the prior for the coefficients
-  prior_intercept = normal(0, 10, autoscale = FALSE), # Set the prior for the intercept
+  prior = normal(0, 0.05, autoscale = FALSE), # Set the prior for the slope coefficient (beta_1)
+  prior_intercept = normal(85, 10, autoscale = FALSE), # Set the prior for the intercept (beta_0)
   seed = 2024 # Set the seed for reproducibility
 )
 

### 2024-03-15 paper/paper.qmd
some syntax modification

@@
 
+## Measurement:
+
+\newpage
+
 ## Data Exploration:
@@
 \begin{align}
-y_i &\sim \mbox{Normal}(\mu_i, \sigma) \
-\mu_i &= \beta_0 + \beta_1 \times \mbox{AGE}_i \
-\beta_0 &\sim \mbox{Normal}(85, 10) \
+y_i &\sim \mbox{Normal}(\mu_i, \sigma) \\
+\mu_i &= \beta_0 + \beta_1 \times \mbox{AGE}_i \\
+\beta_0 &\sim \mbox{Normal}(85, 10) \\
 \beta_1 &\sim \mbox{Normal}(0, 0.05)
@@
 
-\newpage
-
 ## Plot for the linear model
@@
 
-In statistical analysis, the significance of this downward trend is supported by a p-value much lower than the conventional threshold of 0.05, confirming the relationship between building age and evaluation score is not due to random chance.
-However, the plot also reveals that while younger buildings cluster more densely around higher evaluation scores, older buildings exhibit a wider spread of scores.
+The plot also reveals that while younger buildings cluster more densely around higher evaluation scores, older buildings exhibit a wider spread of scores.
 This variation suggests that other factors may influence the condition and safety of older buildings, which are not captured solely by age.

### 2024-03-15 paper/paper.tex
some syntax modification

--- 2024-03-15 paper/paper.qmd
@@
----
-title: "Structural Insights 2023: A Linear Analysis of Apartment Age and Safety Scores in Toronto"
-title-block-banner: true
-abstract: "This study harnesses a dataset from the Toronto Open Data portal, comprising 3,435 records of apartment evaluations, to analyze the correlation between building age and safety scores.
-Employing a linear regression model, we discovered a significant inverse relationship, highlighting that older buildings tend to have lower safety evaluations.
-The findings suggest a need for policy reform, particularly in the maintenance and inspection of Toronto's aging residential infrastructure.
-Despite the study’s focus on building age, further research considering additional variables could offer a more comprehensive understanding of factors influencing building safety."
-thanks: "Code and data supporting this analysis are available at https://github.com/TEJMaster/Toronto-Building-Safety-Analysis-2023.git"
-author: "Terry Tu, Jingyi Shen, Yaning Jin "
-date: today
-date-format: long
-format: pdf
-toc: true
-toc-depth: 1
-number-sections: true
-bibliography: references.bib
-link-citations: true
-editor: 
-  markdown: 
-    wrap: sentence
----
+% Options for packages loaded elsewhere
+\PassOptionsToPackage{unicode}{hyperref}
+\PassOptionsToPackage{hyphens}{url}
+\PassOptionsToPackage{dvipsnames,svgnames,x11names}{xcolor}
+%
+\documentclass[
+  letterpaper,
+  DIV=11,
+  numbers=noendperiod]{scrartcl}
 
-```{r setup, include=FALSE, message=FALSE}
-## Import necessary libraries
-library(ggplot2)
-library(dplyr)
-library(tidyverse)
-library(here)
-library(readr)
-library(knitr)
-library(kableExtra)
-```
+\usepackage{amsmath,amssymb}
+\usepackage{iftex}
+\ifPDFTeX
+  \usepackage[T1]{fontenc}
+  \usepackage[utf8]{inputenc}
+  \usepackage{textcomp} % provide euro and other symbols
+\else % if luatex or xetex
+  \usepackage{unicode-math}
+  \defaultfontfeatures{Scale=MatchLowercase}
+  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
+\fi
+\usepackage{lmodern}
+\ifPDFTeX\else  
+    % xetex/luatex font selection
+\fi
+% Use upquote if available, for straight quotes in verbatim environments
+\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
+\IfFileExists{microtype.sty}{% use microtype if available
+  \usepackage[]{microtype}
+  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
+}{}
+\makeatletter
+\@ifundefined{KOMAClassName}{% if non-KOMA class
+  \IfFileExists{parskip.sty}{%
+    \usepackage{parskip}
+  }{% else
+    \setlength{\parindent}{0pt}
+    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
+}{% if KOMA class
+  \KOMAoptions{parskip=half}}
+\makeatother
+\usepackage{xcolor}
+\setlength{\emergencystretch}{3em} % prevent overfull lines
+\setcounter{secnumdepth}{5}
+% Make \paragraph and \subparagraph free-standing
+\ifx\paragraph\undefined\else
+  \let\oldparagraph\paragraph
+  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
+\fi
+\ifx\subparagraph\undefined\else
+  \let\oldsubparagraph\subparagraph
+  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
+\fi
 
-# Introduction
+\providecommand{\tightlist}{%
+  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}\usepackage{longtable,booktabs,array}
+\usepackage{calc} % for calculating minipage widths
+% Correct order of tables after \paragraph or \subparagraph
+\usepackage{etoolbox}
+\makeatletter
+\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
+\makeatother
+% Allow footnotes in longtable head/foot
+\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
+\makesavenoteenv{longtable}
+\usepackage{graphicx}
+\makeatletter
+\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
+\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
+\makeatother
+% Scale images if necessary, so that they will not overflow the page
+% margins by default, and it is still possible to overwrite the defaults
+% using explicit options in \includegraphics[width, height, ...]{}
+\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
+% Set default figure placement to htbp
+\makeatletter
+\def\fps@figure{htbp}
+\makeatother
+\newlength{\cslhangindent}
+\setlength{\cslhangindent}{1.5em}
+\newlength{\csllabelwidth}
+\setlength{\csllabelwidth}{3em}
+\newlength{\cslentryspacingunit} % times entry-spacing
+\setlength{\cslentryspacingunit}{\parskip}
+\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
+ {% don't indent paragraphs
+  \setlength{\parindent}{0pt}
+  % turn on hanging indent if param 1 is 1
+  \ifodd #1
+  \let\oldpar\par
+  \def\par{\hangindent=\cslhangindent\oldpar}
+  \fi
+  % set entry spacing
+  \setlength{\parskip}{#2\cslentryspacingunit}
+ }%
+ {}
+\usepackage{calc}
+\newcommand{\CSLBlock}[1]{#1\hfill\break}
+\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
+\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
+\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
 
-The structural integrity of urban buildings is a paramount concern for city planners, policymakers, and residents alike.
-The tragic collapse of a condominium in South Florida in June 2021, which resulted in 98 casualties, serves as a stark reminder of the potential consequences of neglecting building maintenance and inspections [@Anderson_2021].
-This event highlights a critical gap in our understanding of the factors that contribute to the safety and longevity of urban residential structures.
-In light of this, our study aims to investigate the relationship between building age and evaluation scores in the context of Toronto's residential buildings.
+\usepackage{booktabs}
+\usepackage{longtable}
+\usepackage{array}
+\usepackage{multirow}
+\usepackage{wrapfig}
+\usepackage{float}
+\usepackage{colortbl}
+\usepackage{pdflscape}
+\usepackage{tabu}
+\usepackage{threeparttable}
+\usepackage{threeparttablex}
+\usepackage[normalem]{ulem}
+\usepackage{makecell}
+\usepackage{xcolor}
+\KOMAoption{captions}{tableheading}
+\makeatletter
+\makeatother
+\makeatletter
+\makeatother
+\makeatletter
+\@ifpackageloaded{caption}{}{\usepackage{caption}}
+\AtBeginDocument{%
+\ifdefined\contentsname
+  \renewcommand*\contentsname{Table of contents}
+\else
+  \newcommand\contentsname{Table of contents}
+\fi
+\ifdefined\listfigurename
+  \renewcommand*\listfigurename{List of Figures}
+\else
+  \newcommand\listfigurename{List of Figures}
+\fi
+\ifdefined\listtablename
+  \renewcommand*\listtablename{List of Tables}
+\else
+  \newcommand\listtablename{List of Tables}
+\fi
+\ifdefined\figurename
+  \renewcommand*\figurename{Figure}
+\else
+  \newcommand\figurename{Figure}
+\fi
+\ifdefined\tablename
+  \renewcommand*\tablename{Table}
+\else
+  \newcommand\tablename{Table}
+\fi
+}
+\@ifpackageloaded{float}{}{\usepackage{float}}
+\floatstyle{ruled}
+\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
+\floatname{codelisting}{Listing}
+\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
+\makeatother
+\makeatletter
+\@ifpackageloaded{caption}{}{\usepackage{caption}}
+\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
+\makeatother
+\makeatletter
+\@ifpackageloaded{tcolorbox}{}{\usepackage[skins,breakable]{tcolorbox}}
+\makeatother
+\makeatletter
+\@ifundefined{shadecolor}{\definecolor{shadecolor}{rgb}{.97, .97, .97}}
+\makeatother
+\makeatletter
+\makeatother
+\makeatletter
+\makeatother
+\ifLuaTeX
+  \usepackage{selnolig}  % disable illegal ligatures
+\fi
+\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
+\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
+\urlstyle{same} % disable monospaced font for URLs
+\hypersetup{
+  pdftitle={Structural Insights 2023: A Linear Analysis of Apartment Age and Safety Scores in Toronto},
+  pdfauthor={Terry Tu, Jingyi Shen, Yaning Jin},
+  colorlinks=true,
+  linkcolor={blue},
+  filecolor={Maroon},
+  citecolor={Blue},
+  urlcolor={Blue},
+  pdfcreator={LaTeX via pandoc}}
 
-Our study's estimand is the effect of building age on evaluation scores in Toronto.
-We investigate how the age of buildings influences their assigned evaluation scores, reflecting their compliance with safety standards and overall condition.
-Utilizing a dataset from the Toronto Open Data portal, which includes 3,435 records, we apply a simple linear regression model to forecast evaluation scores for Toronto residences in 2023.
-By conducting this analysis, we aim to quantify the impact of building age on evaluation scores and understand its implications for urban housing safety and maintenance.
+\title{Structural Insights 2023: A Linear Analysis of Apartment Age and
+Safety Scores in Toronto\thanks{Code and data supporting this analysis
+are available at
+https://github.com/TEJMaster/Toronto-Building-Safety-Analysis-2023.git}}
+\author{Terry Tu, Jingyi Shen, Yaning Jin}
+\date{March 15, 2024}
 
-The analysis reveals a statistically significant inverse relationship between building age and evaluation score, indicating that older buildings tend to receive lower evaluation scores.
-This finding highlights the critical need for regular inspections and maintenance to preserve the safety and habitability of aging buildings.
-It also suggests that policies should prioritize the maintenance and inspection of older structures to prevent potential safety hazards.
+\begin{document}
+\maketitle
+\begin{abstract}
+This study harnesses a dataset from the Toronto Open Data portal,
+comprising 3,435 records of apartment evaluations, to analyze the
+correlation between building age and safety scores. Employing a linear
+regression model, we discovered a significant inverse relationship,
+highlighting that older buildings tend to have lower safety evaluations.
+The findings suggest a need for policy reform, particularly in the
+maintenance and inspection of Toronto's aging residential
+infrastructure. Despite the study's focus on building age, further
+research considering additional variables could offer a more
+comprehensive understanding of factors influencing building safety.
+\end{abstract}
+\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[borderline west={3pt}{0pt}{shadecolor}, sharp corners, interior hidden, breakable, frame hidden, boxrule=0pt, enhanced]}{\end{tcolorbox}}\fi
 
-Moreover, our study offers insights into urban development and maintenance, suggesting that policymakers might need to revisit regulations surrounding building inspections and maintenance schedules.
-It further emphasizes the importance of continuous monitoring and evaluation by urban authorities to maintain and enhance housing standards across the city.
-These insights carry substantial implications for urban planning and public safety, underscoring the necessity of proactive measures to mitigate risks associated with aging infrastructure.
-In conclusion, this paper significantly advances our understanding of the relationship between building age and evaluation scores, underlining the importance of proactive strategies to ensure the safety and integrity of the urban housing stock.
+\renewcommand*\contentsname{Table of contents}
+{
+\hypersetup{linkcolor=}
+\setcounter{tocdepth}{1}
+\tableofcontents
+}
+\hypertarget{introduction}{%
+\section{Introduction}\label{introduction}}
 
-The remainder of this paper is structured as follows: @sec-data (Data) details the raw data, the cleaning process, and provides an overview of the data distribution.
-@sec-model (Model) describes the linear model employed to predict the building evaluation score based on the building's age.
-@sec-result (Results) presents the coefficients of the linear model, analyses the residuals, and includes a plot illustrating the linear model applied to the analysis dataset.
-Finally, @sec-discussion (Discussion) discusses the limitations of the analysis and suggests potential insights for future research.
+The structural integrity of urban buildings is a paramount concern for
+city planners, policymakers, and residents alike. The tragic collapse of
+a condominium in South Florida in June 2021, which resulted in 98
+casualties, serves as a stark reminder of the potential consequences of
+neglecting building maintenance and inspections
+(\protect\hyperlink{ref-Anderson_2021}{Anderson 2021}). This event
+highlights a critical gap in our understanding of the factors that
+contribute to the safety and longevity of urban residential structures.
+In light of this, our study aims to investigate the relationship between
+building age and evaluation scores in the context of Toronto's
+residential buildings.
 
-# Data {#sec-data}
+Our study's estimand is the effect of building age on evaluation scores
+in Toronto. We investigate how the age of buildings influences their
+assigned evaluation scores, reflecting their compliance with safety
+standards and overall condition. Utilizing a dataset from the Toronto
+Open Data portal, which includes 3,435 records, we apply a simple linear
+regression model to forecast evaluation scores for Toronto residences in
+2023. By conducting this analysis, we aim to quantify the impact of
+building age on evaluation scores and understand its implications for
+urban housing safety and maintenance.
 
-```{r include=FALSE, message=FALSE}
-# read the data file and store it in the 'data' variable
-cleaned_data <- read_csv(here("data", "analysis_data", "cleaned_building_data.csv"))
-```
+The analysis reveals a statistically significant inverse relationship
+between building age and evaluation score, indicating that older
+buildings tend to receive lower evaluation scores. This finding
+highlights the critical need for regular inspections and maintenance to
+preserve the safety and habitability of aging buildings. It also
+suggests that policies should prioritize the maintenance and inspection
+of older structures to prevent potential safety hazards.
 
-## Raw Data
+Moreover, our study offers insights into urban development and
+maintenance, suggesting that policymakers might need to revisit
+regulations surrounding building inspections and maintenance schedules.
+It further emphasizes the importance of continuous monitoring and
+evaluation by urban authorities to maintain and enhance housing
+standards across the city. These insights carry substantial implications
+for urban planning and public safety, underscoring the necessity of
+proactive measures to mitigate risks associated with aging
+infrastructure. In conclusion, this paper significantly advances our
+understanding of the relationship between building age and evaluation
+scores, underlining the importance of proactive strategies to ensure the
+safety and integrity of the urban housing stock.
 
-In this research, we examine apartment data sourced using the `opendatatoronto` package [@Toronto_2023].
-The dataset encompasses 3,435 records, focusing on specific variables: the ward of each apartment, its evaluation score, and the construction year.
-The data covers evaluations across Toronto's 25 wards, with scores varying between a minimum of 0 and some achieving the maximum score of 100.
-The study includes apartments that are over three stories in height and contain at least 10 units.
-These apartments span a wide range of construction years, from as early as 1805 to as recent as 2023.
-All the apartments in this dataset adhere to the City's Apartment Building Standards bylaw, which is designed to safeguard the interests and safety of both landlords and tenants by mandating these evaluations.
+The remainder of this paper is structured as follows:
+Section~\ref{sec-data} (Data) details the raw data, the cleaning
+process, and provides an overview of the data distribution.
+Section~\ref{sec-model} (Model) describes the linear model employed to
+predict the building evaluation score based on the building's age.
+Section~\ref{sec-result} (Results) presents the coefficients of the
+linear model, analyses the residuals, and includes a plot illustrating
+the linear model applied to the analysis dataset. Finally,
+Section~\ref{sec-discussion} (Discussion) discusses the limitations of
+the analysis and suggests potential insights for future research.
 
-## Data Analysis Tools
+\hypertarget{sec-data}{%
+\section{Data}\label{sec-data}}
 
-The data analysis was performed using R [@r], a powerful open-source statistical programming language.
-A suite of packages from the tidyverse [@rTidyverse], an assemblage of R packages designed for data science, was harnessed to enhance the efficiency of our data operations.
-The `ggplot2` package [@rGgplot2] facilitated the creation of sophisticated visualizations, while `dplyr` [@rDplyr] provided a grammar of data manipulation, offering a coherent set of verbs that help in filtering, summarizing, and arranging the dataset.
-The `readr` package [@rReadr] was utilized for its fast and friendly data reading capabilities.
-Navigation and file path management were streamlined using the `here` package [@R-here], simplifying the process of file referencing within the project's directory structure.
-Report generation was dynamically handled by knitr [@rKnitr], enabling the integration of R code within this document.
-Additionally, `kableExtra`[@R-kableExtra] was employed to produce aesthetically pleasing and customizable tables, enriching the presentation of our results.
-For the Bayesian analysis, rstanarm [@R-rstanarm] was utilized to create a linear model, providing an elegant interface to Stan, a state-of-the-art platform for statistical modeling and high-performance statistical computation.
-This package enabled us to estimate the relationship between building age and safety evaluation scores using a Bayesian framework.
+\hypertarget{raw-data}{%
+\subsection{Raw Data}\label{raw-data}}
 
-## Variable Description
+In this research, we examine apartment data sourced using the
+\texttt{opendatatoronto} package
+(\protect\hyperlink{ref-Toronto_2023}{Toronto 2023}). The dataset
+encompasses 3,435 records, focusing on specific variables: the ward of
+each apartment, its evaluation score, and the construction year. The
+data covers evaluations across Toronto's 25 wards, with scores varying
+between a minimum of 0 and some achieving the maximum score of 100. The
+study includes apartments that are over three stories in height and
+contain at least 10 units. These apartments span a wide range of
+construction years, from as early as 1805 to as recent as 2023. All the
+apartments in this dataset adhere to the City's Apartment Building
+Standards bylaw, which is designed to safeguard the interests and safety
+of both landlords and tenants by mandating these evaluations.
 
-CURRENT BUILDING EVAL SCORE: The Current Building Evaluation Score represents a measure of a building's adherence to property standards.
-This score is derived by summing two components: the current reactive score, which reflects the compliance based on any outstanding Orders and Notices of Violations, and the proactive building score, which is based on the most recent comprehensive evaluation of the building.
+\hypertarget{data-analysis-tools}{%
+\subsection{Data Analysis Tools}\label{data-analysis-tools}}
 
-YEAR BUILT:	This indicates the year when the building was initially constructed, sourced from Building Owners/Managers.
+The data analysis was performed using R (\protect\hyperlink{ref-r}{R
+Core Team 2022}), a powerful open-source statistical programming
+language. A suite of packages from the tidyverse
+(\protect\hyperlink{ref-rTidyverse}{Wickham et al. 2019}), an assemblage
+of R packages designed for data science, was harnessed to enhance the
+efficiency of our data operations. The \texttt{ggplot2} package
+(\protect\hyperlink{ref-rGgplot2}{Wickham 2016}) facilitated the
+creation of sophisticated visualizations, while \texttt{dplyr}
+(\protect\hyperlink{ref-rDplyr}{Wickham et al. 2022}) provided a grammar
+of data manipulation, offering a coherent set of verbs that help in
+filtering, summarizing, and arranging the dataset. The \texttt{readr}
+package (\protect\hyperlink{ref-rReadr}{Wickham, Hester, and Bryan
+2022}) was utilized for its fast and friendly data reading capabilities.
+Navigation and file path management were streamlined using the
+\texttt{here} package (\protect\hyperlink{ref-R-here}{Müller 2020}),
+simplifying the process of file referencing within the project's
+directory structure. Report generation was dynamically handled by knitr
+(\protect\hyperlink{ref-rKnitr}{Xie 2014}), enabling the integration of
+R code within this document. Additionally,
+\texttt{kableExtra}(\protect\hyperlink{ref-R-kableExtra}{Zhu 2021}) was
+employed to produce aesthetically pleasing and customizable tables,
+enriching the presentation of our results. For the Bayesian analysis,
+rstanarm (\protect\hyperlink{ref-R-rstanarm}{Goodrich et al. 2020}) was
+utilized to create a linear model, providing an elegant interface to
+Stan, a state-of-the-art platform for statistical modeling and
+high-performance statistical computation. This package enabled us to
+estimate the relationship between building age and safety evaluation
+scores using a Bayesian framework.
 
-YEAR EVALUATED: This denotes the year in which the building underwent evaluation, reflecting its condition and performance.
+\hypertarget{variable-description}{%
+\subsection{Variable Description}\label{variable-description}}
 
-AGE: In this research, neither YEAR BUILT nor YEAR EVALUATED was used directly, we have generated a new variable called AGE which use YEAR EVALUATED minus YEAR BUILT.
+CURRENT BUILDING EVAL SCORE: The Current Building Evaluation Score
+represents a measure of a building's adherence to property standards.
+This score is derived by summing two components: the current reactive
+score, which reflects the compliance based on any outstanding Orders and
+Notices of Violations, and the proactive building score, which is based
+on the most recent comprehensive evaluation of the building.
 
-## Sample of Cleaned Building Evaluation Data
+YEAR BUILT: This indicates the year when the building was initially
+constructed, sourced from Building Owners/Managers.
 
-```{r}
-#| label: tbl-data-sample
-#| tbl-cap: Sample of Building Evaluation Data
-#| echo: false
+YEAR EVALUATED: This denotes the year in which the building underwent
+evaluation, reflecting its condition and performance.
 
-sample_data <- head(cleaned_data) %>%
-  select(X_id, AGE, CURRENT.BUILDING.EVAL.SCORE)
+AGE: In this research, neither YEAR BUILT nor YEAR EVALUATED was used
+directly, we have generated a new variable called AGE which use YEAR
+EVALUATED minus YEAR BUILT.
 
-# Create a nicely formatted table with custom column names
-kable(sample_data, col.names = c("Building ID", "Age (Years)", "Evaluation Score"))
-```
-@tbl-data-sample represents a subset of the larger building evaluation data.
-Each row corresponds to a unique building identified by X_id.
-The AGE column indicates the age of the building in years, while the CURRENT.BUILDING.EVAL.SCORE column shows the building's current evaluation score on a scale from 0 to 100, with higher scores indicating better compliance with safety standards.
+\hypertarget{sample-of-cleaned-building-evaluation-data}{%
+\subsection{Sample of Cleaned Building Evaluation
+Data}\label{sample-of-cleaned-building-evaluation-data}}
 
-## Measurement:
+\hypertarget{tbl-data-sample}{}
+\begin{longtable}[]{@{}rrr@{}}
+\caption{\label{tbl-data-sample}Sample of Building Evaluation
+Data}\tabularnewline
+\toprule\noalign{}
+Building ID & Age (Years) & Evaluation Score \\
+\midrule\noalign{}
+\endfirsthead
+\toprule\noalign{}
+Building ID & Age (Years) & Evaluation Score \\
+\midrule\noalign{}
+\endhead
+\bottomrule\noalign{}
+\endlastfoot
+1 & 62 & 86 \\
+2 & 44 & 94 \\
+3 & 54 & 78 \\
+4 & 73 & 89 \\
+5 & 54 & 99 \\
+6 & 53 & 99 \\
+\end{longtable}
+
+Table~\ref{tbl-data-sample} represents a subset of the larger building
+evaluation data. Each row corresponds to a unique building identified by
+X\_id. The AGE column indicates the age of the building in years, while
+the CURRENT.BUILDING.EVAL.SCORE column shows the building's current
+evaluation score on a scale from 0 to 100, with higher scores indicating
+better compliance with safety standards.
+
+\hypertarget{measurement}{%
+\subsection{Measurement:}\label{measurement}}
 
@@
 
-## Data Exploration:
+\hypertarget{data-exploration}{%
+\subsection{Data Exploration:}\label{data-exploration}}
 
-### Data Summary
-```{r}
-#| label: tbl-summary-table
-#| tbl-cap: Summary Statistics for the Cleaned Dataset
-#| echo: false
+\hypertarget{data-summary}{%
+\subsubsection{Data Summary}\label{data-summary}}
 
-summary_data <- cleaned_data %>%
-  summarise(
-    Count = n(),
-    Mean_Age = mean(AGE, na.rm = TRUE),
-    Std_Age = sd(AGE, na.rm = TRUE),
-    Mean_Score = mean(CURRENT.BUILDING.EVAL.SCORE, na.rm = TRUE),
-    Std_Score = sd(CURRENT.BUILDING.EVAL.SCORE, na.rm = TRUE)
-  ) %>%
-  mutate(across(everything(), ~round(., 3)))
+\hypertarget{tbl-summary-table}{}
+\begin{longtable}[t]{>{}ccccc}
+\caption{\label{tbl-summary-table}Summary Statistics for the Cleaned Dataset }\tabularnewline
 
-# Create and print a nicely formatted table
-summary_table <- kable(summary_data, 
-                       col.names = c("Count", "Mean Age (Years)", "SD of Age (Years)", 
-                                     "Mean Score", "SD of Score"), 
-                       align = 'c') %>%
-  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), 
-                full_width = F, 
-                position = "center") %>%
-  column_spec(1, bold = TRUE) # Make the first column bold
+\toprule
+Count & Mean Age (Years) & SD of Age (Years) & Mean Score & SD of Score\\
+\midrule
+\textbf{1748} & 60.644 & 19.939 & 87.504 & 8.693\\
+\bottomrule
+\end{longtable}
 
-# Print the summary table
-summary_table
-```
+Table~\ref{tbl-summary-table} presents a concise overview of the key
+descriptive metrics for the age of buildings and their evaluation scores
+within the dataset:
 
-@tbl-summary-table presents a concise overview of the key descriptive metrics for the age of buildings and their evaluation scores within the dataset:
+\begin{itemize}
+\item
+  \textbf{Count}: The dataset encompasses a total of 1,748 buildings,
+  indicating a robust sample size for statistical analysis.
+\item
+  \textbf{Mean Age}: The average age of the buildings is approximately
+  60.644 years, suggesting that the dataset primarily includes buildings
+  that have been standing for over half a century.
+\item
+  \textbf{Standard Deviation of Age}: With a standard deviation of about
+  19.939 years, there is considerable variability in the ages of the
+  buildings. This range implies a diverse sample, encompassing both
+  relatively new constructions and much older structures.
+\item
+  \textbf{Mean Score}: The average building evaluation score is
+  approximately 87.504 on a scale from 0 to 100. A higher score
+  corresponds to better adherence to safety and maintenance standards,
+  suggesting that the buildings in this dataset are generally
+  well-maintained.
+\item
+  \textbf{Standard Deviation of Score}: The standard deviation of
+  approximately 8.693 for the evaluation scores indicates that while
+  scores are clustered around a high mean, there is still notable
+  variability, reflecting differences in the condition or compliance of
+  the buildings.
+\end{itemize}
 
-- **Count**: The dataset encompasses a total of 1,748 buildings, indicating a robust sample size for statistical analysis.
+These statistics offer a snapshot of the dataset's characteristics,
+providing foundational insights for further analysis regarding the state
+of building safety and integrity in the population studied.
 
-- **Mean Age**: The average age of the buildings is approximately 60.644 years, suggesting that the dataset primarily includes buildings that have been standing for over half a century.
+\hypertarget{age-distribution}{%
+\subsubsection{Age Distribution}\label{age-distribution}}
 
-- **Standard Deviation of Age**: With a standard deviation of about 19.939 years, there is considerable variability in the ages of the buildings.
-This range implies a diverse sample, encompassing both relatively new constructions and much older structures.
+\begin{figure}
 
-- **Mean Score**: The average building evaluation score is approximately 87.504 on a scale from 0 to 100.
-A higher score corresponds to better adherence to safety and maintenance standards, suggesting that the buildings in this dataset are generally well-maintained.
+{\centering \includegraphics{paper_files/figure-pdf/fig-age-distribution-1.pdf}
 
-- **Standard Deviation of Score**: The standard deviation of approximately 8.693 for the evaluation scores indicates that while scores are clustered around a high mean, there is still notable variability, reflecting differences in the condition or compliance of the buildings.
+}
 
-These statistics offer a snapshot of the dataset's characteristics, providing foundational insights for further analysis regarding the state of building safety and integrity in the population studied.
+\caption{\label{fig-age-distribution}Distribution of building's age for
+the cleaned data set}
 
-### Age Distribution
-```{r fig-age-distribution, echo=FALSE, fig.cap="Distribution of building's age for the cleaned data set"}
-# Histogram for the distribution of building age
-ggplot(cleaned_data, aes(x = AGE)) +
-  geom_histogram(binwidth = 5, fill = "steelblue", color = "white") +
-  labs(
-    x = "Age of Building (Years)",
-    y = "Frequency"
-  ) +
-  theme_minimal() +
-  theme(
-    plot.title = element_text(size = 16, face = "bold"),
-    axis.title = element_text(size = 14),
-    axis.text = element_text(size = 12)
-  )
-```
+\end{figure}
 
-@fig-age-distribution illustrates the frequency distribution of the ages of buildings within the dataset.
-The x-axis represents the age of the buildings in years, while the y-axis shows the frequency of buildings within each age range.
-The distribution appears to be unimodal with a peak around the 50-year mark, indicating that a substantial number of the buildings within this dataset were constructed around half a century ago.
-Following this peak, the frequency gradually decreases, showing that fewer buildings have been in existence beyond this age.
-The distribution suggests a relatively young building population, with ages concentrated below 100 years, and very few buildings reaching beyond 120 years of age.
-This visualization aids in understanding the age profile of buildings under consideration for safety evaluation scoring.
+Figure~\ref{fig-age-distribution} illustrates the frequency distribution
+of the ages of buildings within the dataset. The x-axis represents the
+age of the buildings in years, while the y-axis shows the frequency of
+buildings within each age range. The distribution appears to be unimodal
+with a peak around the 50-year mark, indicating that a substantial
+number of the buildings within this dataset were constructed around half
+a century ago. Following this peak, the frequency gradually decreases,
+showing that fewer buildings have been in existence beyond this age. The
+distribution suggests a relatively young building population, with ages
+concentrated below 100 years, and very few buildings reaching beyond 120
+years of age. This visualization aids in understanding the age profile
+of buildings under consideration for safety evaluation scoring.
 
-### Score Distribution
+\hypertarget{score-distribution}{%
+\subsubsection{Score Distribution}\label{score-distribution}}
 
-```{r fig-score-distribution, echo=FALSE, fig.cap="Distribution of building's evaluation score for the cleaned data set"}
-# Histogram for CURRENT.BUILDING.EVAL.SCORE distribution
-ggplot(cleaned_data, aes(x = CURRENT.BUILDING.EVAL.SCORE)) +
-  geom_histogram(binwidth = 5, fill = "darkgreen", color = "white") +
-  labs(
-    x = "Current Building Evaluation Score",
-    y = "Frequency"
-  ) +
-  theme_minimal() +
-  theme(
-    plot.title = element_text(size = 16, face = "bold"),
-    axis.title = element_text(size = 14),
-    axis.text = element_text(size = 12)
-  )
-```
+\begin{figure}
 
-@fig-score-distribution showcases the distribution of building evaluation scores.
-The x-axis represents the scores assigned to buildings, which can range from 0 to 100, with the y-axis displaying the frequency of buildings for each score interval.
-The chart reveals a concentration of high evaluation scores, suggesting that many of the buildings in the dataset are rated as being in good or excellent condition according to the evaluation criteria.
-The tallest bars are clustered towards the higher end of the score range, indicating that buildings with scores close to 100 are prevalent.
-This positive skew in the distribution might reflect effective building standards and maintenance practices in place.
-The spread of the scores and their frequency can offer insights into the overall health of the evaluated buildings, influencing urban planning and policy development.
+{\centering \includegraphics{paper_files/figure-pdf/fig-score-distribution-1.pdf}
 
-# Model {#sec-model}
+}
 
-The objective of our model is dual: to discern the relationship between building age and safety evaluation scores and to quantify this relationship's strength and direction.
-The study utilizes a simple linear regression model to analyze the dataset obtained from the Toronto Open Data portal.
+\caption{\label{fig-score-distribution}Distribution of building's
+evaluation score for the cleaned data set}
 
-## Model set-up
+\end{figure}
 
-Let $y_i$ represent the safety evaluation score for each building. The building's age is denoted by $x_i$.The model is defined as follows:
+Figure~\ref{fig-score-distribution} showcases the distribution of
+building evaluation scores. The x-axis represents the scores assigned to
+buildings, which can range from 0 to 100, with the y-axis displaying the
+frequency of buildings for each score interval. The chart reveals a
+concentration of high evaluation scores, suggesting that many of the
+buildings in the dataset are rated as being in good or excellent
+condition according to the evaluation criteria. The tallest bars are
+clustered towards the higher end of the score range, indicating that
+buildings with scores close to 100 are prevalent. This positive skew in
+the distribution might reflect effective building standards and
+maintenance practices in place. The spread of the scores and their
+frequency can offer insights into the overall health of the evaluated
+buildings, influencing urban planning and policy development.
+
+\hypertarget{sec-model}{%
+\section{Model}\label{sec-model}}
+
+The objective of our model is dual: to discern the relationship between
+building age and safety evaluation scores and to quantify this
+relationship's strength and direction. The study utilizes a simple
+linear regression model to analyze the dataset obtained from the Toronto
+Open Data portal.
+
+\hypertarget{model-set-up}{%
+\subsection{Model set-up}\label{model-set-up}}
+
+Let \(y_i\) represent the safety evaluation score for each building. The
+building's age is denoted by \(x_i\).The model is defined as follows:
 
@@
 
-The model is implemented in R using the rstanarm package, which allows us to incorporate prior beliefs about the parameters and to estimate the posterior distributions.
-For the intercept $\beta_0$ and slope $\beta_1$ , we choose normal prior distributions centered around our initial estimates based on exploratory data analysis.
-The `stan_glm` function from `rstanarm` is utilized to carry out the Bayesian regression, providing a framework for inference that incorporates both the data and our prior knowledge.
+The model is implemented in R using the rstanarm package, which allows
+us to incorporate prior beliefs about the parameters and to estimate the
+posterior distributions. For the intercept \(\beta_0\) and slope
+\(\beta_1\) , we choose normal prior distributions centered around our
+initial estimates based on exploratory data analysis. The
+\texttt{stan\_glm} function from \texttt{rstanarm} is utilized to carry
+out the Bayesian regression, providing a framework for inference that
+incorporates both the data and our prior knowledge.
 
-The priors are chosen to reflect reasonable beliefs about the parameters before observing the data.
-The intercept prior reflects an expectation that a new building will have a high safety score around 90, with a wide spread to accommodate uncertainty.
-Similarly, the slope prior indicates an expected small negative impact of age on the safety score, acknowledging some uncertainty in the precise effect.
-The `stan_glm` function combines these priors with the data to estimate the posterior distributions of the model parameters.
+The priors are chosen to reflect reasonable beliefs about the parameters
+before observing the data. The intercept prior reflects an expectation
+that a new building will have a high safety score around 90, with a wide
+spread to accommodate uncertainty. Similarly, the slope prior indicates
+an expected small negative impact of age on the safety score,
+acknowledging some uncertainty in the precise effect. The
+\texttt{stan\_glm} function combines these priors with the data to
+estimate the posterior distributions of the model parameters.
 
-## Model justification
+\hypertarget{model-justification}{%
+\subsection{Model justification}\label{model-justification}}
 
-We hypothesize that the coefficient for building age ($\beta_1$) will be negative, reflecting the tendency for older buildings to exhibit lower safety scores.
-This expectation is rooted in the general understanding that buildings can deteriorate over time due to wear, aging materials, and possible obsolescence in older construction methods.
-The intercept ($\beta_0$), representing the baseline evaluation score for a new building, is presumed to be relatively high, indicating the score a building would receive if it were built in the current period with modern standards.
-The slope ($\beta_1$) is therefore of particular interest, as it encapsulates the average annual decline in evaluation score attributable to aging.
-The Bayesian framework allows us to incorporate these hypotheses as priors in our model, thereby aligning the analysis with our substantive expectations and providing a more nuanced interpretation of the data.
+We hypothesize that the coefficient for building age (\(\beta_1\)) will
+be negative, reflecting the tendency for older buildings to exhibit
+lower safety scores. This expectation is rooted in the general
+understanding that buildings can deteriorate over time due to wear,
+aging materials, and possible obsolescence in older construction
+methods. The intercept (\(\beta_0\)), representing the baseline
+evaluation score for a new building, is presumed to be relatively high,
+indicating the score a building would receive if it were built in the
+current period with modern standards. The slope (\(\beta_1\)) is
+therefore of particular interest, as it encapsulates the average annual
+decline in evaluation score attributable to aging. The Bayesian
+framework allows us to incorporate these hypotheses as priors in our
+model, thereby aligning the analysis with our substantive expectations
+and providing a more nuanced interpretation of the data.
 
-# Result {#sec-result}
+\hypertarget{sec-result}{%
+\section{Result}\label{sec-result}}
 
-```{r echo=FALSE}
-# Retrieve the Bayesian linear model from the saved .rds file
-bayesian_model <- readRDS(file = here("models", "bayesian_linear_model.rds"))
-```
+\hypertarget{model-coefficients-interpretation}{%
+\subsection{Model Coefficients
+Interpretation}\label{model-coefficients-interpretation}}
 
-## Model Coefficients Interpretation
+\hypertarget{tbl-coefficient-table}{}
+\begin{longtable}[t]{cc}
+\caption{\label{tbl-coefficient-table}Summary Statistics for the Coefficients of the Linear Model }\tabularnewline
 
-```{r}
-#| label: tbl-coefficient-table
-#| tbl-cap: Summary Statistics for the Coefficients of the Linear Model
-#| echo: false
+\toprule
+Term & Estimate\\
+\midrule
+Intercept & 93.364\\
+Slope & -0.097\\
+\bottomrule
+\end{longtable}
 
-# Extract coefficients from the Bayesian model
-coefficients <- coef(bayesian_model)
+Table~\ref{tbl-coefficient-table} provides two key coefficients to
+understand the relationship between building age and the evaluation
+score:
 
-# Convert coefficients to a data frame for better formatting
-coefficients_df <- data.frame(
-  Term = c("Intercept", "Slope"),
-  Estimate = unname(coefficients) 
-)
+\textbf{Intercept} (\(\beta_0\)):\\
+The model's intercept, \(\beta_0\), has an estimate of 93.364. This
+represents the baseline evaluation score for a hypothetical newly
+constructed building. The intercept suggests that if a building were
+constructed in the current year, its expected evaluation score would be
+around 93.364, assuming all other factors remain constant.
 
-# Round the estimates to three digits
-coefficients_df$Estimate <- round(coefficients_df$Estimate, 3)
+\textbf{Slope} (\(\beta_1\)):\\
+The slope parameter, \(\beta_1\), has an estimate of -0.097. This
+indicates that, on average, the evaluation score is expected to decrease
+by approximately 0.097 points for each additional year of a building's
+age. This negative value suggests a trend where older buildings tend to
+have lower evaluation scores compared to newer ones.
 
-# Create a nicely formatted table
-coefficient_table <- kable(coefficients_df,
-                           col.names = c("Term", "Estimate"),
-                           align = 'c') %>%
-  kable_styling(bootstrap_options = c("striped", "hover", "condensed"),
-                full_width = FALSE,
-                position = "center")
+\textbf{Interpretation}: The analysis suggests a negative relationship
+between building age and evaluation score. The estimates indicate that
+newer buildings tend to have higher evaluation scores, which decrease as
+buildings age. This trend highlights the importance of age as a factor
+in building evaluations and underscores the need for ongoing maintenance
+and updates to preserve building safety and integrity over time.
 
-# Print the summary table
-coefficient_table
-```
-
-@tbl-coefficient-table provides two key coefficients to understand the relationship between building age and the evaluation score:
-
-**Intercept** ($\beta_0$):  
-The model's intercept, $\beta_0$, has an estimate of 93.364.
-This represents the baseline evaluation score for a hypothetical newly constructed building.
-The intercept suggests that if a building were constructed in the current year, its expected evaluation score would be around 93.364, assuming all other factors remain constant.
-
-**Slope** ($\beta_1$):  
-The slope parameter, $\beta_1$, has an estimate of -0.097.
-This indicates that, on average, the evaluation score is expected to decrease by approximately 0.097 points for each additional year of a building's age.
-This negative value suggests a trend where older buildings tend to have lower evaluation scores compared to newer ones.
-
-**Interpretation**:
-The analysis suggests a negative relationship between building age and evaluation score.
-The estimates indicate that newer buildings tend to have higher evaluation scores, which decrease as buildings age.
-This trend highlights the importance of age as a factor in building evaluations and underscores the need for ongoing maintenance and updates to preserve building safety and integrity over time.
-
-## Model Equation
+\hypertarget{model-equation}{%
+\subsection{Model Equation}\label{model-equation}}
 
@@
 
-In this model, $y_i$ represents the predicted evaluation score for the $i$-th building, $x_i$ represents the age for the $i$-th building, $\mu_i$ is the mean of the normal distribution for the $i$-th observation, $\beta_0$ is the intercept, and $\beta_1$ is the slope representing the change in evaluation score per year of building age.
+In this model, \(y_i\) represents the predicted evaluation score for the
+\(i\)-th building, \(x_i\) represents the age for the \(i\)-th building,
+\(\mu_i\) is the mean of the normal distribution for the \(i\)-th
+observation, \(\beta_0\) is the intercept, and \(\beta_1\) is the slope
+representing the change in evaluation score per year of building age.
 
-## Analysis of Residuals
+\hypertarget{analysis-of-residuals}{%
+\subsection{Analysis of Residuals}\label{analysis-of-residuals}}
 
-```{r}
-#| label: tbl-residuals-summary
-#| tbl-cap: Summary Statistics for the Residuals of the Bayesian Linear Model
-#| echo: false
+\hypertarget{tbl-residuals-summary}{}
+\begin{longtable}[]{@{}cc@{}}
+\caption{\label{tbl-residuals-summary}Summary Statistics for the
+Residuals of the Bayesian Linear Model}\tabularnewline
+\toprule\noalign{}
+Residual Statistics & Value \\
+\midrule\noalign{}
+\endfirsthead
+\toprule\noalign{}
+Residual Statistics & Value \\
+\midrule\noalign{}
+\endhead
+\bottomrule\noalign{}
+\endlastfoot
+Min & -69.700 \\
+1st Qu. & -4.440 \\
+Median & 1.687 \\
+Mean & -0.003 \\
+3rd Qu. & 5.860 \\
+Max & 15.715 \\
+\end{longtable}
 
-# Extract residuals from the Bayesian model
-residuals <- residuals(bayesian_model)
+\textbf{1. Minimum Residual}: The minimum residual is -69.700,
+indicating that there is at least one building for which the model's
+predicted evaluation score was lower than the actual score by
+approximately 69.700 points. This could be an outlier or a building with
+exceptional characteristics not captured by the model.
 
-# Create a summary table for residuals and round to three digits
-residuals_rounded <- round(summary(residuals), 3)
+\textbf{2. First Quartile Residual}: The first quartile (Q1) of the
+residuals is -4.440, meaning that 25\% of the buildings have evaluation
+scores that are less than 4.440 points below the model's prediction for
+their age.
 
-# Create a data frame for better formatting
-residuals_summary_df <- data.frame(
-  Statistic = c("Min", "1st Qu.", "Median", "Mean", "3rd Qu.", "Max"),
-  Value = as.numeric(residuals_rounded)  # Convert to numeric to ensure proper formatting
-)
+\textbf{3. Median Residual}: The median residual is 1.687, suggesting a
+slight positive bias in the model's predictions, as the median of the
+error distribution is above zero. This indicates that, on average, the
+model tends to slightly overestimate the evaluation scores.
 
-# Create a nicely formatted table
-residuals_table <- kable(residuals_summary_df,
-                         col.names = c("Residual Statistics", "Value"),
-                         align = 'c')
+\textbf{4. Third Quartile Residual}: The third quartile (Q3) is 5.860,
+indicating that 75\% of the buildings have evaluation scores within
+5.860 points of the model's predictions or better. This shows that the
+model provides reasonably accurate predictions for the majority of
+buildings.
 
-# Print the summary table
-residuals_table
-```
+\textbf{5. Maximum Residual}: The maximum residual is 15.715, suggesting
+that there is at least one building for which the model's predicted
+evaluation score was higher than the actual score by approximately
+15.715 points. This could be another outlier or a building that
+performed exceptionally well.
 
-**1.
-Minimum Residual**: The minimum residual is -69.700, indicating that there is at least one building for which the model's predicted evaluation score was lower than the actual score by approximately 69.700 points.
-This could be an outlier or a building with exceptional characteristics not captured by the model.
+\textbf{Interpretation}: The residuals provide insights into the model's
+fit and the distribution of errors. The presence of outliers and the
+distribution's slight asymmetry warrant further investigation. It's
+crucial to assess the model's assumptions, such as linearity,
+homoscedasticity, and normality of residuals, to ensure the validity of
+the statistical inferences made from the model. Understanding the
+reasons behind significant deviations can help improve the model and
+provide more accurate predictions.
 
-**2.
-First Quartile Residual**: The first quartile (Q1) of the residuals is -4.440, meaning that 25% of the buildings have evaluation scores that are less than 4.440 points below the model's prediction for their age.
+\hypertarget{plot-for-the-linear-model}{%
+\subsection{Plot for the linear model}\label{plot-for-the-linear-model}}
 
-**3.
-Median Residual**: The median residual is 1.687, suggesting a slight positive bias in the model's predictions, as the median of the error distribution is above zero.
-This indicates that, on average, the model tends to slightly overestimate the evaluation scores.
+\begin{figure}
 
-**4.
-Third Quartile Residual**: The third quartile (Q3) is 5.860, indicating that 75% of the buildings have evaluation scores within 5.860 points of the model's predictions or better.
-This shows that the model provides reasonably accurate predictions for the majority of buildings.
+{\centering \includegraphics{paper_files/figure-pdf/fig-linear-plot-1.pdf}
 
-**5.
-Maximum Residual**: The maximum residual is 15.715, suggesting that there is at least one building for which the model's predicted evaluation score was higher than the actual score by approximately 15.715 points.
-This could be another outlier or a building that performed exceptionally well.
+}
 
-**Interpretation**: The residuals provide insights into the model's fit and the distribution of errors.
-The presence of outliers and the distribution's slight asymmetry warrant further investigation.
-It's crucial to assess the model's assumptions, such as linearity, homoscedasticity, and normality of residuals, to ensure the validity of the statistical inferences made from the model.
-Understanding the reasons behind significant deviations can help improve the model and provide more accurate predictions.
+\caption{\label{fig-linear-plot}plot for the linear relationship between
+building age and evaluation score}
 
-## Plot for the linear model
-```{r fig-linear-plot, echo=FALSE, warning=FALSE, message=FALSE, fig.cap="plot for the linear relationship between building age and evaluation score"}
-# Enhanced scatter plot with regression line
-improved_plot <- ggplot(cleaned_data, aes(x = AGE, y = CURRENT.BUILDING.EVAL.SCORE)) +
-  geom_point(alpha = 0.7, size = 1) +  # Adjust transparency and size of points
-  geom_smooth(method = "lm", color = "blue", size = 1) +  
-  labs(
-    x = "Building Age",
-    y = "Building Evaluation Score",
-    title = "Impact of Building Age on Evaluation Score"
-  ) +
-  theme_minimal() +  # Use a minimal theme
-  theme(
-    plot.title = element_text(size = 14),
-    axis.title.x = element_text(size = 12),
-    axis.title.y = element_text(size = 12),
-    axis.text.x = element_text(angle = 45, hjust = 1),
-    axis.text.y = element_text(size = 10),
-    legend.position = "none"  # Hide the legend if not necessary
-  )
+\end{figure}
 
-# Display the plot
-print(improved_plot)
-```
+Figure~\ref{fig-linear-plot} provides a clear visual relationship
+between the age of buildings and their evaluation scores. Displayed with
+building age on the x-axis and evaluation score on the y-axis, the data
+points represent individual apartment buildings. The blue line running
+through the cluster of points represents the linear regression line,
+which captures the average effect of age on evaluation score.
+Noticeably, the slope of the line is downward, suggesting a negative
+correlation; as the buildings get older, their evaluation scores tend to
+decrease. This trend is consistent across the dataset, indicating a
+general decline in scores as building age increases, a reflection of the
+typical effects of wear and time on building integrity.
 
-@fig-linear-plot provides a clear visual relationship between the age of buildings and their evaluation scores.
-Displayed with building age on the x-axis and evaluation score on the y-axis, the data points represent individual apartment buildings.
-The blue line running through the cluster of points represents the linear regression line, which captures the average effect of age on evaluation score.
-Noticeably, the slope of the line is downward, suggesting a negative correlation; as the buildings get older, their evaluation scores tend to decrease.
-This trend is consistent across the dataset, indicating a general decline in scores as building age increases, a reflection of the typical effects of wear and time on building integrity.
+The plot also reveals that while younger buildings cluster more densely
+around higher evaluation scores, older buildings exhibit a wider spread
+of scores. This variation suggests that other factors may influence the
+condition and safety of older buildings, which are not captured solely
+by age. The plot does not show any clear pattern or funnel shape in the
+residuals, indicating that the variance of the evaluation scores is
+fairly consistent across the range of building ages, and the assumption
+of homoscedasticity is not visibly violated. Nonetheless, the model's
+findings imply the importance of consistent maintenance and updates to
+older buildings to ensure safety standards are upheld over time.
 
-The plot also reveals that while younger buildings cluster more densely around higher evaluation scores, older buildings exhibit a wider spread of scores.
-This variation suggests that other factors may influence the condition and safety of older buildings, which are not captured solely by age.
-The plot does not show any clear pattern or funnel shape in the residuals, indicating that the variance of the evaluation scores is fairly consistent across the range of building ages, and the assumption of homoscedasticity is not visibly violated.
-Nonetheless, the model's findings imply the importance of consistent maintenance and updates to older buildings to ensure safety standards are upheld over time.
+\hypertarget{sec-discussion}{%
+\section{Discussion}\label{sec-discussion}}
 
-# Discussion {#sec-discussion}
+\hypertarget{overview-of-the-study}{%
+\subsection{Overview of the Study}\label{overview-of-the-study}}
 
-## Overview of the Study
+This paper presented a detailed analysis using simple linear regression
+to investigate the impact of building age on the evaluation scores
+assigned by the City of Toronto. By analyzing data from the Toronto Open
+Data portal, the study aimed to forecast evaluation scores for Toronto
+residences in 2023. The analysis revealed a statistically significant
+inverse relationship between building age and evaluation score,
+suggesting that older buildings tend to have lower evaluation scores.
 
-This paper presented a detailed analysis using simple linear regression to investigate the impact of building age on the evaluation scores assigned by the City of Toronto.
-By analyzing data from the Toronto Open Data portal, the study aimed to forecast evaluation scores for Toronto residences in 2023.
-The analysis revealed a statistically significant inverse relationship between building age and evaluation score, suggesting that older buildings tend to have lower evaluation scores.
+\hypertarget{insights-into-urban-development-and-maintenance}{%
+\subsection{Insights into Urban Development and
+Maintenance}\label{insights-into-urban-development-and-maintenance}}
 
-## Insights into Urban Development and Maintenance
+One key insight from this study is the importance of building age in the
+overall health and safety of urban residential environments. The
+findings underscore the potential risks associated with older buildings,
+which may not meet modern standards or may have deteriorated over time.
+This knowledge emphasizes the need for regular inspections, maintenance,
+and upgrades to older buildings to ensure they remain safe and
+habitable. Additionally, the study highlights the value of continuous
+monitoring and evaluation by urban authorities to maintain and improve
+housing standards across the city.
 
-One key insight from this study is the importance of building age in the overall health and safety of urban residential environments.
-The findings underscore the potential risks associated with older buildings, which may not meet modern standards or may have deteriorated over time.
-This knowledge emphasizes the need for regular inspections, maintenance, and upgrades to older buildings to ensure they remain safe and habitable.
-Additionally, the study highlights the value of continuous monitoring and evaluation by urban authorities to maintain and improve housing standards across the city.
+\hypertarget{policy-implications-and-housing-quality}{%
+\subsection{Policy Implications and Housing
+Quality}\label{policy-implications-and-housing-quality}}
 
-## Policy Implications and Housing Quality
+Another significant insight relates to the policy implications for
+housing quality and safety standards. The correlation between building
+age and lower evaluation scores may prompt policymakers to reconsider
+regulations surrounding building inspections, maintenance schedules, and
+renovation requirements. It suggests an opportunity for targeted
+interventions in older buildings to prevent potential hazards and
+improve living conditions for residents. Moreover, these findings could
+guide urban planning strategies, prioritizing the revitalization of
+aging housing stock and ensuring equitable access to safe and quality
+housing.
 
-Another significant insight relates to the policy implications for housing quality and safety standards.
-The correlation between building age and lower evaluation scores may prompt policymakers to reconsider regulations surrounding building inspections, maintenance schedules, and renovation requirements.
-It suggests an opportunity for targeted interventions in older buildings to prevent potential hazards and improve living conditions for residents.
-Moreover, these findings could guide urban planning strategies, prioritizing the revitalization of aging housing stock and ensuring equitable access to safe and quality housing.
+\hypertarget{limitations-of-the-study}{%
+\subsection{Limitations of the Study}\label{limitations-of-the-study}}
 
-## Limitations of the Study
+Despite its contributions, this study has several limitations. Firstly,
+the model accounts for only a small fraction of the variability in
+evaluation scores, indicating that other factors besides building age
+significantly influence these scores. The exclusion of variables such as
+building materials, design, maintenance history, and location may limit
+the comprehensiveness of the findings. Additionally, the model's
+assumptions (e.g., linearity and homoscedasticity) and the presence of
+outliers suggest caution in generalizing the results without further
+investigation.
 
-Despite its contributions, this study has several limitations.
-Firstly, the model accounts for only a small fraction of the variability in evaluation scores, indicating that other factors besides building age significantly influence these scores.
-The exclusion of variables such as building materials, design, maintenance history, and location may limit the comprehensiveness of the findings.
-Additionally, the model's assumptions (e.g., linearity and homoscedasticity) and the presence of outliers suggest caution in generalizing the results without further investigation.
+\hypertarget{future-directions}{%
+\subsection{Future Directions}\label{future-directions}}
 
-## Future Directions
+Given the limitations and the insights gained, future research should
+aim to incorporate additional variables that could affect building
+evaluation scores. A more comprehensive model including factors like
+renovation history, compliance with current building codes, and
+socio-economic characteristics of the neighborhood could provide a
+deeper understanding of what influences building evaluation scores.
+Longitudinal studies could also shed light on the trends over time,
+offering insights into the effectiveness of policy interventions and
+maintenance practices. Moreover, comparative analyses across different
+cities or countries could highlight unique challenges and best practices
+in building maintenance and safety standards.
 
-Given the limitations and the insights gained, future research should aim to incorporate additional variables that could affect building evaluation scores.
-A more comprehensive model including factors like renovation history, compliance with current building codes, and socio-economic characteristics of the neighborhood could provide a deeper understanding of what influences building evaluation scores.
-Longitudinal studies could also shed light on the trends over time, offering insights into the effectiveness of policy interventions and maintenance practices.
-Moreover, comparative analyses across different cities or countries could highlight unique challenges and best practices in building maintenance and safety standards.
+In conclusion, while this study has provided valuable insights into the
+impact of building age on evaluation scores, it also opens the door for
+further research to explore the multifaceted nature of building quality
+and safety. Addressing these questions is crucial for developing
+effective strategies to improve urban living conditions and ensure the
+longevity and safety of the housing stock.
 
-In conclusion, while this study has provided valuable insights into the impact of building age on evaluation scores, it also opens the door for further research to explore the multifaceted nature of building quality and safety.
-Addressing these questions is crucial for developing effective strategies to improve urban living conditions and ensure the longevity and safety of the housing stock.
+\hypertarget{appendix}{%
+\section{Appendix}\label{appendix}}
 
-# Appendix
+\hypertarget{references}{%
+\section*{References}\label{references}}
+\addcontentsline{toc}{section}{References}
 
-# References
+\hypertarget{refs}{}
+\begin{CSLReferences}{1}{0}
+\leavevmode\vadjust pre{\hypertarget{ref-Anderson_2021}{}}%
+Anderson, Curt. 2021. {``Lawsuit Claims Surfside Condo Collapse
+Triggered by Building Work.''} \emph{NBC 6 South Florida}. NBC 6 South
+Florida.
+\href{http://www.nbcmiami.com/news/local/lawsuit-claims-surfside-condo-collapse-triggered-by-building-w\%20ork/2622574/.}{http://www.nbcmiami.com/news/local/lawsuit-claims-surfside-condo-collapse-triggered-by-building-w
+ork/2622574/.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-R-rstanarm}{}}%
+Goodrich, Ben, Jonah Gabry, Imad Ali, and Sam Brilleman. 2020.
+\emph{Rstanarm: Bayesian Applied Regression Modeling via Stan}.
+\url{https://mc-stan.org/rstanarm}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-R-here}{}}%
+Müller, Kirill. 2020. \emph{Here: A Simpler Way to Find Your Files}.
+\url{https://CRAN.R-project.org/package=here}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-r}{}}%
+R Core Team. 2022. \emph{R: A Language and Environment for Statistical
+Computing}. Vienna, Austria: R Foundation for Statistical Computing.
+\url{https://www.R-project.org/}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-Toronto_2023}{}}%
+Toronto, City of. 2023. {``Open Data.''} \emph{City of Toronto}.
+\url{https://www.toronto.ca/city-government/data-research-maps/open-data/}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-rGgplot2}{}}%
+Wickham, Hadley. 2016. \emph{Ggplot2: Elegant Graphics for Data
+Analysis}. Springer-Verlag New York.
+\url{https://ggplot2.tidyverse.org}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-rTidyverse}{}}%
+Wickham, Hadley, Mara Averick, Jennifer Bryan, Winston Chang, Lucy
+D'Agostino McGowan, Romain François, Garrett Grolemund, et al. 2019.
+{``Welcome to the {tidyverse}.''} \emph{Journal of Open Source Software}
+4 (43): 1686. \url{https://doi.org/10.21105/joss.01686}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-rDplyr}{}}%
+Wickham, Hadley, Romain François, Lionel Henry, and Kirill Müller. 2022.
+\emph{Dplyr: A Grammar of Data Manipulation}.
+\url{https://CRAN.R-project.org/package=dplyr}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-rReadr}{}}%
+Wickham, Hadley, Jim Hester, and Jennifer Bryan. 2022. \emph{Readr: Read
+Rectangular Text Data}. \url{https://CRAN.R-project.org/package=readr}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-rKnitr}{}}%
+Xie, Yihui. 2014. {``Knitr: A Comprehensive Tool for Reproducible
+Research in {R}.''} In \emph{Implementing Reproducible Computational
+Research}, edited by Victoria Stodden, Friedrich Leisch, and Roger D.
+Peng. Chapman; Hall/CRC.
+\url{http://www.crcpress.com/product/isbn/9781466561595}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-R-kableExtra}{}}%
+Zhu, Hao. 2021. \emph{kableExtra: Construct Complex Table with 'Kable'
+and Pipe Syntax}. \url{https://CRAN.R-project.org/package=kableExtra}.
+
+\end{CSLReferences}
+
+\end{document}

### 2024-03-16 paper/paper.qmd
modified measurement, discussion

@@
 ## Measurement:
+
+For our research, we collected data from the City of Toronto’s website utilizing the "opendatatoronto" package [@Toronto_2023].
+We adjusted certain variables and excluded observations with missing values, as several variables were incomplete.
+A new variable, "AGE" was introduced to represent the building's age, which served as the sole predictor in our simple linear regression analysis.
+
+Apartment Building Standards program was initiated in 2017 to ensure that apartment buildings with at least three stories or 10 units adhere to required maintenance standards.
+This initiative targets building owners and operators, ensuring compliance through regular inspections.
+
+This dataset provides scores from these evaluations for registered RentSafeTO buildings, where Bylaw Enforcement Officers inspect areas like common spaces, mechanical and security features, parking, and exterior grounds.
+
+In 2023, the evaluation method of RentSafeTO saw significant changes.
+Now, buildings are assessed at minimum every two years, with the inclusion of 50 different categories in the evaluation, each given a specific weight.
+
+During an evaluation, each category is scored on a scale from one to three, with one being the lowest score and three the highest.
+Occasionally, a category might receive a score of 0 if it’s not possible to evaluate it due to blockages or refusal of access.
+If a category is not relevant at the time of evaluation, it's left blank in the dataset.
 
@@
 
-## Overview of the Study
+## Summary of Findings
 
-This paper presented a detailed analysis using simple linear regression to investigate the impact of building age on the evaluation scores assigned by the City of Toronto.
-By analyzing data from the Toronto Open Data portal, the study aimed to forecast evaluation scores for Toronto residences in 2023.
-The analysis revealed a statistically significant inverse relationship between building age and evaluation score, suggesting that older buildings tend to have lower evaluation scores.
+This study embarked on a journey to understand the relationship between the age of apartment buildings in Toronto and their safety evaluation scores.
+Leveraging a dataset of 3,435 records from the Toronto Open Data portal, we employed simple linear regression analysis to unearth a significant inverse correlation between building age and safety scores.
+Specifically, our findings indicate that older buildings in Toronto tend to receive lower safety evaluation scores.
+This observation underscores the potential risks associated with aging infrastructure, aligning with the broader literature on building safety and maintenance.
 
-## Insights into Urban Development and Maintenance
+## Insights into Building Safety
 
-One key insight from this study is the importance of building age in the overall health and safety of urban residential environments.
-The findings underscore the potential risks associated with older buildings, which may not meet modern standards or may have deteriorated over time.
-This knowledge emphasizes the need for regular inspections, maintenance, and upgrades to older buildings to ensure they remain safe and habitable.
-Additionally, the study highlights the value of continuous monitoring and evaluation by urban authorities to maintain and improve housing standards across the city.
+Our analysis brings to light a critical insight into the urban infrastructure landscape: the aging of buildings could be a ticking time bomb if not properly managed.
+The negative correlation between building age and evaluation scores signals that older buildings may not meet current safety and maintenance standards compared to newer constructions.
+This poses a significant challenge for city planners, policymakers, and building owners alike, emphasizing the need for regular inspections, maintenance, and renovations to ensure that these structures remain safe for occupancy.
 
-## Policy Implications and Housing Quality
+## Policy Implications
 
-Another significant insight relates to the policy implications for housing quality and safety standards.
-The correlation between building age and lower evaluation scores may prompt policymakers to reconsider regulations surrounding building inspections, maintenance schedules, and renovation requirements.
-It suggests an opportunity for targeted interventions in older buildings to prevent potential hazards and improve living conditions for residents.
-Moreover, these findings could guide urban planning strategies, prioritizing the revitalization of aging housing stock and ensuring equitable access to safe and quality housing.
+The findings of this study have profound implications for public policy and regulatory frameworks.
+They suggest a need for revisiting and possibly tightening regulations concerning building inspections and maintenance, especially for older structures.
+Moreover, the results could inform the development of targeted policies that prioritize interventions in older buildings, potentially including incentives for owners to upgrade and maintain their properties to meet current safety standards.
+Implementing such policies could significantly reduce the risks associated with structural failures, thereby enhancing urban safety and resilience.
 
-## Limitations of the Study
+## Limitations and Areas for Improvement
 
-Despite its contributions, this study has several limitations.
-Firstly, the model accounts for only a small fraction of the variability in evaluation scores, indicating that other factors besides building age significantly influence these scores.
-The exclusion of variables such as building materials, design, maintenance history, and location may limit the comprehensiveness of the findings.
-Additionally, the model's assumptions (e.g., linearity and homoscedasticity) and the presence of outliers suggest caution in generalizing the results without further investigation.
+While our study provides valuable insights, it is not without limitations.
+The primary focus on building age as the sole predictor of safety scores overlooks other potential factors that might influence these scores, such as the materials used in construction, the building's design, and the history of renovations and repairs.
+Additionally, the linear regression model, though powerful in detecting linear relationships, may not capture non-linear dynamics that could be present between building age and safety scores.
 
-## Future Directions
+Future research should consider incorporating more variables into the analysis to capture a broader spectrum of factors influencing building safety.
+Moreover, employing more complex models, such as multivariate regression or machine learning algorithms, could unveil more nuanced relationships and provide a more comprehensive understanding of what determines building safety scores.
 
-Given the limitations and the insights gained, future research should aim to incorporate additional variables that could affect building evaluation scores.
-A more comprehensive model including factors like renovation history, compliance with current building codes, and socio-economic characteristics of the neighborhood could provide a deeper understanding of what influences building evaluation scores.
-Longitudinal studies could also shed light on the trends over time, offering insights into the effectiveness of policy interventions and maintenance practices.
-Moreover, comparative analyses across different cities or countries could highlight unique challenges and best practices in building maintenance and safety standards.
+## Forward Look: Beyond Age
 
-In conclusion, while this study has provided valuable insights into the impact of building age on evaluation scores, it also opens the door for further research to explore the multifaceted nature of building quality and safety.
-Addressing these questions is crucial for developing effective strategies to improve urban living conditions and ensure the longevity and safety of the housing stock.
+This study marks a starting point in the exploration of factors influencing building safety in Toronto.
+As we move forward, it is crucial to broaden our analytical lens to include a wider array of variables that could affect building safety.
+Investigating the role of renovation histories, compliance with evolving building codes, and the impact of environmental factors such as climate change could enrich our understanding.
+Additionally, comparative studies across different cities or countries could reveal interesting insights into how various regulatory frameworks and building practices impact safety outcomes.
+
+Ultimately, enhancing building safety is a complex challenge that requires a multifaceted approach, combining rigorous research, policy innovation, and community engagement.
+Our study contributes to this ongoing conversation, highlighting the urgency of addressing the risks associated with aging urban infrastructures.
+As we look to the future, let us draw upon the lessons learned from this research to build safer, more resilient communities for all.
 

### 2024-03-16 paper/paper.qmd
added appendix

@@
 
+## Data Cleaning
+
+The data cleaning process involved several key steps to prepare the building evaluation dataset for analysis.
+Initially, the dataset was loaded into a data frame, and entries with missing values in the YEAR.BUILT and YEAR.EVALUATED columns were removed to ensure the accuracy of subsequent calculations.
+This step was essential to maintain the integrity of the dataset.
+Next, the age of each building was calculated by subtracting the year it was built from the year it was evaluated, and this information was added to the dataset as a new column, AGE.
+The cleaned dataset, now free of missing values and containing the calculated ages, was saved as a CSV file in the 'analysis_data' directory for further analysis.
+This thorough cleaning process was crucial for ensuring the reliability of the study's findings and laying a solid foundation for the statistical modeling that followed.
+
+## Data Validation
+
+Following the data cleaning process, a series of data integrity tests were conducted on the cleaned building evaluation dataset to ensure its accuracy and reliability for analysis.
+The first test verified that there were no negative values in the AGE column, as negative building ages would be illogical.
+The second test confirmed the absence of missing values (NA) in the critical columns YEAR.BUILT, YEAR.EVALUATED, and CURRENT.BUILDING.EVAL.SCORE, which are essential for the analysis.
+The third test checked that all evaluation scores fell within the expected range of 0 to 100, a necessary condition for valid score data.
+Lastly, the fourth test ensured that all buildings were evaluated in the year 2023, aligning with the study's focus on contemporary building evaluations.
+These validation checks were crucial for maintaining the dataset's integrity and provided confidence in the subsequent statistical modeling and analysis.
+
 # References

### 2024-03-16 paper/paper.qmd
new measurement

@@
 
-For our research, we collected data from the City of Toronto’s website utilizing the "opendatatoronto" package [@Toronto_2023].
-We adjusted certain variables and excluded observations with missing values, as several variables were incomplete.
-A new variable, "AGE" was introduced to represent the building's age, which served as the sole predictor in our simple linear regression analysis.
+In this study, we utilized data from the City of Toronto's RentSafeTO program, accessed through the "opendatatoronto" package [@Toronto_2023].
+The RentSafeTO program, initiated in 2017, aims to ensure that apartment buildings with at least three stories or 10 units meet essential safety and maintenance standards.
+This program is crucial for enhancing resident living conditions and extending the longevity of buildings in Toronto [@rentsafeto].
 
-Apartment Building Standards program was initiated in 2017 to ensure that apartment buildings with at least three stories or 10 units adhere to required maintenance standards.
-This initiative targets building owners and operators, ensuring compliance through regular inspections.
+To prepare the dataset for analysis, we made several adjustments, including the introduction of a new variable, "AGE," which represents the age of the building and serves as the sole predictor in our simple linear regression analysis.
+We also excluded observations with missing values to ensure the completeness of our dataset.
 
-This dataset provides scores from these evaluations for registered RentSafeTO buildings, where Bylaw Enforcement Officers inspect areas like common spaces, mechanical and security features, parking, and exterior grounds.
+The RentSafeTO program involves regular evaluations conducted by Bylaw Enforcement Officers, who assess various aspects of buildings, including common areas, mechanical and security systems, and exteriors.
+In 2023, the evaluation process was updated to require biennial evaluations, expand the assessment categories to 50, and introduce a scoring system ranging from zero to three.
+This updated process addresses previous challenges in evaluations and non-applicabilities, providing a more comprehensive and nuanced understanding of building conditions.
 
-In 2023, the evaluation method of RentSafeTO saw significant changes.
-Now, buildings are assessed at minimum every two years, with the inclusion of 50 different categories in the evaluation, each given a specific weight.
-
-During an evaluation, each category is scored on a scale from one to three, with one being the lowest score and three the highest.
-Occasionally, a category might receive a score of 0 if it’s not possible to evaluate it due to blockages or refusal of access.
-If a category is not relevant at the time of evaluation, it's left blank in the dataset.
-
-\newpage
+The dataset resulting from these evaluations offers valuable insights into the dynamics of building aging within Toronto's regulatory and maintenance framework.
+It is particularly useful for researchers and analysts looking to investigate temporal trends and the impact of the post-2023 enhancements on building safety and maintenance standards.
 
@@
 ### Age Distribution
-```{r fig-age-distribution, echo=FALSE, fig.cap="Distribution of building's age for the cleaned data set"}
+```{r fig-age-distribution, echo=FALSE, fig.cap="Distribution of building's age for the cleaned data set", fig.width=8, fig.height=4}
 # Histogram for the distribution of building age
@@
   theme(
-    plot.title = element_text(size = 16, face = "bold"),
-    axis.title = element_text(size = 14),
-    axis.text = element_text(size = 12)
+    plot.title = element_text(size = 10, face = "bold"),
+    axis.title = element_text(size = 9),
+    axis.text = element_text(size = 8)
   )
@@
 
+\newpage
 ### Score Distribution
 
-```{r fig-score-distribution, echo=FALSE, fig.cap="Distribution of building's evaluation score for the cleaned data set"}
+```{r fig-score-distribution, echo=FALSE, fig.cap="Distribution of building's evaluation score for the cleaned data set", fig.width=8, fig.height=4}
+# Code created with the help from ChatGPT
 # Histogram for CURRENT.BUILDING.EVAL.SCORE distribution

### 2024-03-16 paper/paper.qmd
changed data section

@@
 
-In this research, we examine apartment data sourced using the `opendatatoronto` package [@Toronto_2023].
+In this research, we examine apartment data sourced using the opendatatoronto package [@Toronto_2023].
 The dataset encompasses 3,435 records, focusing on specific variables: the ward of each apartment, its evaluation score, and the construction year.
@@
 These apartments span a wide range of construction years, from as early as 1805 to as recent as 2023.
+
 All the apartments in this dataset adhere to the City's Apartment Building Standards bylaw, which is designed to safeguard the interests and safety of both landlords and tenants by mandating these evaluations.
+Although we have access to the building evaluation datasets from previous years, we chose to analyze the most recent data to ensure our study reflects the current state of apartment building scores in Toronto.
+This approach allows us to provide up-to-date insights into the relationship between building age and evaluation scores, which is critical for informing policy and maintenance practices in the city.
 
@@
 
-CURRENT BUILDING EVAL SCORE: The Current Building Evaluation Score represents a measure of a building's adherence to property standards.
-This score is derived by summing two components: the current reactive score, which reflects the compliance based on any outstanding Orders and Notices of Violations, and the proactive building score, which is based on the most recent comprehensive evaluation of the building.
+**CURRENT BUILDING EVAL SCORE**: The Current Building Evaluation Score represents a measure of a building's adherence to property standards.
+This score is derived by summing two components: the current reactive score, which reflects the compliance based on any outstanding Orders and Notices of Violations, and the proactive building score, which is based on the most recent comprehensive evaluation of the building [@Toronto_2023b].
 
-YEAR BUILT:	This indicates the year when the building was initially constructed, sourced from Building Owners/Managers.
+**YEAR BUILT**:	This indicates the year when the building was initially constructed, sourced from Building Owners/Managers.
 
-YEAR EVALUATED: This denotes the year in which the building underwent evaluation, reflecting its condition and performance.
+**YEAR EVALUATED**: This denotes the year in which the building underwent evaluation, reflecting its condition and performance.
 
-AGE: In this research, neither YEAR BUILT nor YEAR EVALUATED was used directly, we have generated a new variable called AGE which use YEAR EVALUATED minus YEAR BUILT.
+**AGE**: In this research, neither YEAR BUILT nor YEAR EVALUATED was used directly, we have generated a new variable called AGE which use YEAR EVALUATED minus YEAR BUILT.
 
@@
 #| echo: false
-
+# Code created with the help from ChatGPT
 sample_data <- head(cleaned_data) %>%
@@
 #| echo: false
-
+# Code created with the help from ChatGPT
 summary_data <- cleaned_data %>%
@@
 ```{r fig-age-distribution, echo=FALSE, fig.cap="Distribution of building's age for the cleaned data set", fig.width=8, fig.height=4}
+# Code created with the help from ChatGPT
 # Histogram for the distribution of building age
@@
 #| echo: false
-
+# Code created with the help from ChatGPT
 # Extract coefficients from the Bayesian model
@@
 #| echo: false
-
+# Code created with the help from ChatGPT
 # Extract residuals from the Bayesian model
@@
 ```{r fig-linear-plot, echo=FALSE, warning=FALSE, message=FALSE, fig.cap="plot for the linear relationship between building age and evaluation score"}
+# Code created with the help from ChatGPT
 # Enhanced scatter plot with regression line

### 2024-03-16 paper/paper.qmd
modification based on comment

@@
 We investigate how the age of buildings influences their assigned evaluation scores, reflecting their compliance with safety standards and overall condition.
-Utilizing a dataset from the Toronto Open Data portal, which includes 3,435 records, we apply a simple linear regression model to forecast evaluation scores for Toronto residences in 2023.
+Utilizing a dataset from the Toronto Open Data portal, which includes 1,758 records, we apply a simple linear regression model to forecast evaluation scores for Toronto residences in 2023.
 By conducting this analysis, we aim to quantify the impact of building age on evaluation scores and understand its implications for urban housing safety and maintenance.
@@
 In this research, we examine apartment data sourced using the opendatatoronto package [@Toronto_2023].
-The dataset encompasses 3,435 records, focusing on specific variables: the ward of each apartment, its evaluation score, and the construction year.
+The dataset encompasses 1,758 records (1,748 records after cleaning), focusing on specific variables: the ward of each apartment, its evaluation score, and the construction year.
 The data covers evaluations across Toronto's 25 wards, with scores varying between a minimum of 0 and some achieving the maximum score of 100.
@@
 
-## Variable Description
+## Variable Description {#sec-variable}
 
@@
 We also excluded observations with missing values to ensure the completeness of our dataset.
+Detailed variable description can be find at @sec-variable.
 
@@
 **1.
-Minimum Residual**: The minimum residual is -69.700, indicating that there is at least one building for which the model's predicted evaluation score was lower than the actual score by approximately 69.700 points.
+Minimum Residual**: The minimum residual is approximately -69.700, indicating that there is at least one building for which the model's predicted evaluation score was lower than the actual score by approximately 69.700 points.
 This could be an outlier or a building with exceptional characteristics not captured by the model.
@@
 **2.
-First Quartile Residual**: The first quartile (Q1) of the residuals is -4.440, meaning that 25% of the buildings have evaluation scores that are less than 4.440 points below the model's prediction for their age.
+First Quartile Residual**: The first quartile (Q1) of the residuals is approximately -4.440, meaning that 25% of the buildings have evaluation scores that are less than 4.440 points below the model's prediction for their age.
 
 **3.
-Median Residual**: The median residual is 1.687, suggesting a slight positive bias in the model's predictions, as the median of the error distribution is above zero.
+Median Residual**: The median residual is approximately 1.687, suggesting a slight positive bias in the model's predictions, as the median of the error distribution is above zero.
 This indicates that, on average, the model tends to slightly overestimate the evaluation scores.
@@
 **4.
-Third Quartile Residual**: The third quartile (Q3) is 5.860, indicating that 75% of the buildings have evaluation scores within 5.860 points of the model's predictions or better.
+Third Quartile Residual**: The third quartile (Q3) is approximately 5.860, indicating that 75% of the buildings have evaluation scores within 5.860 points of the model's predictions or better.
 This shows that the model provides reasonably accurate predictions for the majority of buildings.
@@
 **5.
-Maximum Residual**: The maximum residual is 15.715, suggesting that there is at least one building for which the model's predicted evaluation score was higher than the actual score by approximately 15.715 points.
+Maximum Residual**: The maximum residual is approximately 15.715, suggesting that there is at least one building for which the model's predicted evaluation score was higher than the actual score by approximately 15.715 points.
 This could be another outlier or a building that performed exceptionally well.
@@
 
-## Forward Look: Beyond Age
+In addition to previously mentioned limitations, the study examining the correlation between the age of apartment buildings in Toronto and their safety evaluation scores may face further constraints due to a variety of factors.
+One significant issue is sampling bias, where the dataset might not uniformly represent all building types, particularly if it disproportionately includes certain structures (such as residential over commercial) or concentrates on specific locales within Toronto, potentially leading to skewed outcomes.
+Another concern is data quality issues stemming from the Toronto Open Data portal, which could feature outdated records, missing details, or errors in data recording, thereby affecting the analysis's accuracy and dependability.
+The voluntary nature of surveys or reporting mechanisms used to collect data on building safety evaluations could also introduce bias, as buildings with higher safety scores might be more inclined to report than those with lower scores, possibly distorting the results.
+
+## Sources of Bias
+
+One potential source of bias in our analysis stems from the nature of the evaluation scores.
+These scores are determined by human evaluators, which introduces a subjective element to the assessment.
+Consequently, the scores might not accurately reflect the true condition of a building.
+Factors such as the evaluator's experience, training, and even their mood on the day of the evaluation can influence the scores assigned.
+Furthermore, inconsistencies in evaluation criteria or their application across different evaluators or buildings could lead to variability in scores that is not related to the actual condition of the buildings.
+This subjectivity and potential for inconsistency can introduce bias into our analysis, as the evaluation scores may not be a perfect representation of a building's safety and maintenance standards.
+It is important to consider these limitations when interpreting the results of our study and to approach the findings with cautio
+
+## Comparion with Similar Studies
+
+To compare our results with similar studies, we looked at the findings from a study conducted by Matthew Wankiewicz titled "Apartment Age is a Strong Predictor for Overall Quality" Wankiewicz, 2020 [@Wankiewicz_2020].
+In this study, Wankiewicz explored the impact of apartment age on the scores assigned by the City of Toronto.
+Similar to our findings, Wankiewicz's analysis revealed a strong and linear relationship between the age of apartments and their evaluation scores, with older apartments tending to score lower.
+This supports our conclusion that the age of a building is a significant predictor of its evaluation score.
+
+## Looking Forward: Beyond Age
 

### 2024-03-16 scripts/02_cleanup-data.R

@@ -16,14 +16,16 @@ library(here)
 # Load the raw data file into a data frame
 data <- read_csv(here("data", "raw_data", "building_evaluation_data.csv"))
 
-# Clean up the data by filtering out NAs in YEAR.BUILT and YEAR.EVALUATED and adding the 'AGE' column
+# Clean up the data by filtering out NAs in YEAR.BUILT, YEAR.EVALUATED, and CURRENT.BUILDING.EVAL.SCORE
+# and adding the 'AGE' column
 cleaned_data <- data %>%
-  filter(!is.na(YEAR.BUILT) & !is.na(YEAR.EVALUATED)) %>%
-  mutate(AGE = YEAR.EVALUATED - YEAR.BUILT)
+  filter(!is.na(YEAR.BUILT) & !is.na(YEAR.EVALUATED) & !is.na(CURRENT.BUILDING.EVAL.SCORE)) %>%
+  mutate(AGE = YEAR.EVALUATED - YEAR.BUILT) %>%
+  select(X_id, YEAR.BUILT, YEAR.EVALUATED, AGE, CURRENT.BUILDING.EVAL.SCORE)
 
 #### Save cleaned data ####
-# Save the cleaned data to a CSV file in the 'outputs/data' directory
+# Save the cleaned data with only the necessary columns to a CSV file in the 'data/analysis_data' directory
 write_csv(cleaned_data, here("data", "analysis_data", "cleaned_building_data.csv"))
 
 # Print a message indicating completion
-cat("Cleaned data has been saved as 'cleaned_building_data.csv' in the 'data/analysis_data' directory")
+cat("Cleaned data with necessary columns has been saved as 'cleaned_building_data.csv' in the 'data/analysis_data' directory")

### 2024-03-16 paper/paper.qmd
grammar issue
modified records

@@
 title-block-banner: true
-abstract: "This study harnesses a dataset from the Toronto Open Data portal, comprising 3,435 records of apartment evaluations, to analyze the correlation between building age and safety scores.
+abstract: "This study harnesses a dataset from the Toronto Open Data portal, comprising 1,758 records of apartment evaluations, to analyze the correlation between building age and safety scores.
 Employing a linear regression model, we discovered a significant inverse relationship, highlighting that older buildings tend to have lower safety evaluations.
@@
 We also excluded observations with missing values to ensure the completeness of our dataset.
-Detailed variable description can be find at @sec-variable.
+Detailed variable descriptions can be found at @sec-variable.
 

### 2024-03-17 paper/paper.qmd
added posterior check

@@
 library(kableExtra)
+library(rstanarm)
 ```
@@
 We investigate how the age of buildings influences their assigned evaluation scores, reflecting their compliance with safety standards and overall condition.
-Utilizing a dataset from the Toronto Open Data portal, which includes 1,758 records, we apply a simple linear regression model to forecast evaluation scores for Toronto residences in 2023.
+Utilizing a dataset from the Toronto Open Data portal [@Toronto_2023], which includes 1,758 records, we apply a simple linear regression model to forecast evaluation scores for Toronto residences in 2023.
 By conducting this analysis, we aim to quantify the impact of building age on evaluation scores and understand its implications for urban housing safety and maintenance.
@@
 These apartments span a wide range of construction years, from as early as 1805 to as recent as 2023.
+For description of the data cleaning process and data validation checks performed, please refer to @sec-appendix (Appendix).
 
@@
 
-## Data Exploration:
+## Data Exploration: {#sec-exploration}
 
@@
 
-- **Count**: The dataset encompasses a total of 1,748 buildings, indicating a robust sample size for statistical analysis.
+- **Count**: The analysis dataset encompasses a total of 1,748 buildings, indicating a robust sample size for statistical analysis.
 
@@
 The study utilizes a simple linear regression model to analyze the dataset obtained from the Toronto Open Data portal.
+Additional details and diagnostics for this model are included in @sec-posterior.
 
@@
 \begin{align}
-y_i &\sim \mbox{Normal}(\mu_i, \sigma) \\
-\mu_i &= \beta_0 + \beta_1 \times \mbox{AGE}_i \\
-\beta_0 &\sim \mbox{Normal}(85, 10) \\
-\beta_1 &\sim \mbox{Normal}(0, 0.05)
+y_i | \mu_i, \sigma &\sim \mbox{Normal}(\mu_i, \sigma) \\
+\mu_i &= \beta_0 + \beta_1 \times x_i \\
+\beta_0 &\sim \mbox{Normal}(90, 10) \\
+\beta_1 &\sim \mbox{Normal}(-0.1, 0.05) \\
+\sigma &\sim \mbox{Exponential}(1)
 \end{align}
 
-The model is implemented in R using the rstanarm package, which allows us to incorporate prior beliefs about the parameters and to estimate the posterior distributions.
-For the intercept $\beta_0$ and slope $\beta_1$ , we choose normal prior distributions centered around our initial estimates based on exploratory data analysis.
+The model is implemented in R using the `rstanarm` package, which allows us to incorporate prior beliefs about the parameters and to estimate the posterior distributions.
+For the intercept $\beta_0$ and slope $\beta_1$, we choose normal prior distributions centered around our initial estimates based on exploratory data analysis (@sec-exploration).
 The `stan_glm` function from `rstanarm` is utilized to carry out the Bayesian regression, providing a framework for inference that incorporates both the data and our prior knowledge.
@@
 Similarly, the slope prior indicates an expected small negative impact of age on the safety score, acknowledging some uncertainty in the precise effect.
+The standard deviation $\sigma$ is given an exponential prior with a rate of 1, reflecting a belief in the likelihood of smaller variability in evaluation scores.
 The `stan_glm` function combines these priors with the data to estimate the posterior distributions of the model parameters.
@@
 **Intercept** ($\beta_0$):  
-The model's intercept, $\beta_0$, has an estimate of 93.364.
+The model's intercept, $\beta_0$, has an estimate of 93.607.
 This represents the baseline evaluation score for a hypothetical newly constructed building.
-The intercept suggests that if a building were constructed in the current year, its expected evaluation score would be around 93.364, assuming all other factors remain constant.
+The intercept suggests that if a building were constructed in the year for evaluation, its expected evaluation score would be around 93.607, assuming all other factors remain constant.
 
 **Slope** ($\beta_1$):  
-The slope parameter, $\beta_1$, has an estimate of -0.097.
-This indicates that, on average, the evaluation score is expected to decrease by approximately 0.097 points for each additional year of a building's age.
+The slope parameter, $\beta_1$, has an estimate of -0.100.
+This indicates that, on average, the evaluation score is expected to decrease by approximately 0.100 points for each additional year of a building's age.
 This negative value suggests a trend where older buildings tend to have lower evaluation scores compared to newer ones.
@@
 \begin{align}
-y_i &\sim \mbox{Normal}(\mu_i, \sigma) \\
-\mu_i &= \beta_0 + \beta_1 \times x_i \\
-\beta_0 &= 93.364 \\
-\beta_1 &= -0.097
+y_i &= 93.607 - 0.100 x_i + \varepsilon_i
 \end{align}
 
-In this model, $y_i$ represents the predicted evaluation score for the $i$-th building, $x_i$ represents the age for the $i$-th building, $\mu_i$ is the mean of the normal distribution for the $i$-th observation, $\beta_0$ is the intercept, and $\beta_1$ is the slope representing the change in evaluation score per year of building age.
+The above model equation serves as a predictive tool, estimating a building's evaluation score based on its age.
+In this equation, $y_i$ is the estimated evaluation score, $x_i$ represents the age of the building, $\varepsilon_i$ captures the residual effect—factors influencing the score that are not explained by the building's age.
+This implies that even among buildings of similar ages, scores can differ based on variables like maintenance quality, renovations, or compliance with updated building codes.
+The equation recognizes that while age is a significant predictor, the complexity of real-world conditions means there's always an element of variability unexplained by age alone.
 
@@
 **1.
-Minimum Residual**: The minimum residual is approximately -69.700, indicating that there is at least one building for which the model's predicted evaluation score was lower than the actual score by approximately 69.700 points.
+Minimum Residual**: The minimum residual is approximately -69.676, indicating that there is at least one building for which the model's predicted evaluation score was lower than the actual score by approximately 69.676 points.
 This could be an outlier or a building with exceptional characteristics not captured by the model.
@@
 **2.
-First Quartile Residual**: The first quartile (Q1) of the residuals is approximately -4.440, meaning that 25% of the buildings have evaluation scores that are less than 4.440 points below the model's prediction for their age.
+First Quartile Residual**: The first quartile (Q1) of the residuals is approximately -4.377, meaning that 25% of the buildings have evaluation scores that are less than 4.377 points below the model's prediction for their age.
 
 **3.
-Median Residual**: The median residual is approximately 1.687, suggesting a slight positive bias in the model's predictions, as the median of the error distribution is above zero.
+Median Residual**: The median residual is approximately 1.705, suggesting a slight positive bias in the model's predictions, as the median of the error distribution is above zero.
 This indicates that, on average, the model tends to slightly overestimate the evaluation scores.
@@
 **4.
-Third Quartile Residual**: The third quartile (Q3) is approximately 5.860, indicating that 75% of the buildings have evaluation scores within 5.860 points of the model's predictions or better.
+Third Quartile Residual**: The third quartile (Q3) is approximately 5.821, indicating that 75% of the buildings have evaluation scores within 5.821 points of the model's predictions or better.
 This shows that the model provides reasonably accurate predictions for the majority of buildings.
@@
 **5.
-Maximum Residual**: The maximum residual is approximately 15.715, suggesting that there is at least one building for which the model's predicted evaluation score was higher than the actual score by approximately 15.715 points.
+Maximum Residual**: The maximum residual is approximately 15.835, suggesting that there is at least one building for which the model's predicted evaluation score was higher than the actual score by approximately 15.835 points.
 This could be another outlier or a building that performed exceptionally well.
@@
     y = "Building Evaluation Score",
-    title = "Impact of Building Age on Evaluation Score"
   ) +
@@
   theme(
-    plot.title = element_text(size = 14),
     axis.title.x = element_text(size = 12),
@@
 This study embarked on a journey to understand the relationship between the age of apartment buildings in Toronto and their safety evaluation scores.
-Leveraging a dataset of 3,435 records from the Toronto Open Data portal, we employed simple linear regression analysis to unearth a significant inverse correlation between building age and safety scores.
+Leveraging a dataset of 1,758 records from the Toronto Open Data portal, we employed simple linear regression analysis to unearth a significant inverse correlation between building age and safety scores.
 Specifically, our findings indicate that older buildings in Toronto tend to receive lower safety evaluation scores.
@@
 
-# Appendix
+# Appendix {#sec-appendix}
 
@@
 
+## Posterior Predictive Check {#sec-posterior}
+
+```{r fig-posterior-plot, echo=FALSE, fig.cap="comparison between observed evaluation scores with those generated by our Bayesian model"}
+# This code generates plot that compare the distribution of the observed data to the distributions implied by the posterior predictive distribution of the model
+pp_check(bayesian_model) + 
+  theme_classic() +
+  theme(legend.position = "bottom")
+```
+From @fig-posterior-plot, we observe that the simulated data from the posterior distribution (represented by the lighter lines) closely match the distribution of the observed data (depicted by the solid line).
+This suggests that our model has a good fit to the observed data and that the chosen priors and model structure can reasonably replicate the variations in evaluation scores across buildings.
+The spread of the lighter lines around the solid line also highlights the degree of uncertainty in our predictions, which is a natural aspect of modeling real-world phenomena.
+
+```{r fig-comparison-plot, echo=FALSE, message=FALSE, fig.cap="Comparison of posterior and prior distributions for model parameters"}
+posterior_vs_prior(bayesian_model) +
+  theme_minimal() +
+  scale_color_brewer(palette = "Set1") +
+  theme(legend.position = "bottom") +
+  coord_flip()
+```
+
+@fig-comparison-plot displays the median and spread of prior and posterior distributions for our model's parameters.
+It shows the posterior for the slope, related to the building's age, is quite similar to the prior, meaning our initial guess was on target.
+For the intercept and sigma, the data has slightly adjusted our estimates, reflecting its informative value.
+Overall, the data confirmed our prior thoughts about the effect of age on the building's evaluation score without much alteration.
+
+\newpage
+
 # References

### 2024-03-17 scripts/04_model.R

@@ -23,8 +23,9 @@ bayesian_model <- stan_glm(
   CURRENT.BUILDING.EVAL.SCORE ~ AGE, 
   data = cleaned_data,
   family = gaussian(), # Assuming a normal distribution for the response variable
-  prior = normal(0, 0.05, autoscale = FALSE), # Set the prior for the slope coefficient (beta_1)
-  prior_intercept = normal(85, 10, autoscale = FALSE), # Set the prior for the intercept (beta_0)
+  prior = normal(-0.1, 0.05), # Set the prior for the slope coefficient (beta_1)
+  prior_intercept = normal(90, 10), # Set the prior for the intercept (beta_0)
+  prior_aux = exponential(rate = 1), # Set the prior for the error term (sigma)
   seed = 2024 # Set the seed for reproducibility
 )
 

### 2024-03-17 paper/paper.qmd
grammar issue

@@
 Despite the study’s focus on building age, further research considering additional variables could offer a more comprehensive understanding of factors influencing building safety."
-thanks: "Code and data supporting this analysis are available at https://github.com/TEJMaster/Toronto-Building-Safety-Analysis-2023.git"
+thanks: "Code and data supporting this analysis are available at https://github.com/TEJMaster/Toronto-Building-Safety-Analysis-2023"
 author: "Terry Tu, Jingyi Shen, Yaning Jin "
@@
 
-The structural integrity of urban buildings is a paramount concern for city planners, policymakers, and residents alike.
-The tragic collapse of a condominium in South Florida in June 2021, which resulted in 98 casualties, serves as a stark reminder of the potential consequences of neglecting building maintenance and inspections [@Anderson_2021].
-This event highlights a critical gap in our understanding of the factors that contribute to the safety and longevity of urban residential structures.
-In light of this, our study aims to investigate the relationship between building age and evaluation scores in the context of Toronto's residential buildings.
+The structural integrity of urban buildings is always the topmost concern for city planners, policymakers, and residents alike.
+The tragic collapse of a condominium in South Florida in June 2021, which resulted in 98 casualties, serves as a reminder of the potential consequences of neglecting building maintenance and inspections [@Anderson_2021].
+This event highlights a critical gap in our understanding of the factors contributing to urban residential structures' safety and lifespan.
+In light of this, our study aims to investigate the relationship between building age and evaluation scores in the context of Toronto's apartment buildings.
 
@@
 This finding highlights the critical need for regular inspections and maintenance to preserve the safety and habitability of aging buildings.
-It also suggests that policies should prioritize the maintenance and inspection of older structures to prevent potential safety hazards.
+It also suggests that policies should prioritize maintaining and inspecting older structures to prevent potential safety hazards.
 
@@
 
-The remainder of this paper is structured as follows: @sec-data (Data) details the raw data, the cleaning process, and provides an overview of the data distribution.
+The remainder of this paper is structured as follows: @sec-data (Data) details the raw data and the cleaning process and provides an overview of the data distribution.
 @sec-model (Model) describes the linear model employed to predict the building evaluation score based on the building's age.
-@sec-result (Results) presents the coefficients of the linear model, analyses the residuals, and includes a plot illustrating the linear model applied to the analysis dataset.
+@sec-result (Results) presents the linear model coefficients, analyses the residuals, and includes a plot illustrating the linear model applied to the analysis dataset.
 Finally, @sec-discussion (Discussion) discusses the limitations of the analysis and suggests potential insights for future research.
@@
 These apartments span a wide range of construction years, from as early as 1805 to as recent as 2023.
-For description of the data cleaning process and data validation checks performed, please refer to @sec-appendix (Appendix).
+For the description of the data cleaning process and data validation checks performed, please refer to @sec-appendix (Appendix).
 
@@
 Additionally, `kableExtra`[@R-kableExtra] was employed to produce aesthetically pleasing and customizable tables, enriching the presentation of our results.
-For the Bayesian analysis, rstanarm [@R-rstanarm] was utilized to create a linear model, providing an elegant interface to Stan, a state-of-the-art platform for statistical modeling and high-performance statistical computation.
+For the Bayesian analysis, rstanarm [@R-rstanarm] was utilized to create a linear model, providing an elegant interface to Stan, a state-of-the-art platform for statistical modelling and high-performance statistical computation.
 This package enabled us to estimate the relationship between building age and safety evaluation scores using a Bayesian framework.
@@
 
-To prepare the dataset for analysis, we made several adjustments, including the introduction of a new variable, "AGE," which represents the age of the building and serves as the sole predictor in our simple linear regression analysis.
-We also excluded observations with missing values to ensure the completeness of our dataset.
-Detailed variable descriptions can be found at @sec-variable.
-
 The RentSafeTO program involves regular evaluations conducted by Bylaw Enforcement Officers, who assess various aspects of buildings, including common areas, mechanical and security systems, and exteriors.
@@
 The dataset resulting from these evaluations offers valuable insights into the dynamics of building aging within Toronto's regulatory and maintenance framework.
-It is particularly useful for researchers and analysts looking to investigate temporal trends and the impact of the post-2023 enhancements on building safety and maintenance standards.
+It is beneficial for researchers and analysts looking to investigate temporal trends and the impact of the post-2023 enhancements on building safety and maintenance standards.
+
+To prepare the dataset for analysis, we made several adjustments, including the introduction of a new variable, "AGE," which represents the age of the building and serves as the sole predictor in our simple linear regression analysis.
+We also excluded observations with missing values to ensure the completeness of our dataset.
+Detailed variable descriptions can be found at @sec-variable.
 
@@
 The x-axis represents the age of the buildings in years, while the y-axis shows the frequency of buildings within each age range.
-The distribution appears to be unimodal with a peak around the 50-year mark, indicating that a substantial number of the buildings within this dataset were constructed around half a century ago.
-Following this peak, the frequency gradually decreases, showing that fewer buildings have been in existence beyond this age.
-The distribution suggests a relatively young building population, with ages concentrated below 100 years, and very few buildings reaching beyond 120 years of age.
+The distribution appears unimodal, with a peak around the 60-year mark, indicating that a substantial number of the buildings within this dataset were constructed more than half a century ago.
+Following this peak, the frequency gradually decreases, showing that fewer and fewer buildings exist beyond this age.
+The distribution suggests a relatively young building population, with ages concentrated below 100 years and very few buildings reaching beyond 120 years of age.
 This visualization aids in understanding the age profile of buildings under consideration for safety evaluation scoring.
@@
 @fig-score-distribution showcases the distribution of building evaluation scores.
-The x-axis represents the scores assigned to buildings, which can range from 0 to 100, with the y-axis displaying the frequency of buildings for each score interval.
-The chart reveals a concentration of high evaluation scores, suggesting that many of the buildings in the dataset are rated as being in good or excellent condition according to the evaluation criteria.
+The x-axis represents the scores assigned to buildings, ranging from 0 to 100, with the y-axis displaying the frequency of buildings for each score interval.
+The chart reveals a concentration of high evaluation scores, suggesting that many of the buildings in the dataset are rated as in good or excellent condition according to the evaluation criteria.
 The tallest bars are clustered towards the higher end of the score range, indicating that buildings with scores close to 100 are prevalent.
 This positive skew in the distribution might reflect effective building standards and maintenance practices in place.
-The spread of the scores and their frequency can offer insights into the overall health of the evaluated buildings, influencing urban planning and policy development.
+The scores' spread and frequency can offer insights into the overall health of the evaluated buildings, influencing urban planning and policy development.
 
@@
 The priors are chosen to reflect reasonable beliefs about the parameters before observing the data.
-The intercept prior reflects an expectation that a new building will have a high safety score around 90, with a wide spread to accommodate uncertainty.
+The intercept prior reflects an expectation that a new building will have a high safety score of around 90, with a widespread to accommodate uncertainty.
 Similarly, the slope prior indicates an expected small negative impact of age on the safety score, acknowledging some uncertainty in the precise effect.
@@
 The intercept ($\beta_0$), representing the baseline evaluation score for a new building, is presumed to be relatively high, indicating the score a building would receive if it were built in the current period with modern standards.
-The slope ($\beta_1$) is therefore of particular interest, as it encapsulates the average annual decline in evaluation score attributable to aging.
-The Bayesian framework allows us to incorporate these hypotheses as priors in our model, thereby aligning the analysis with our substantive expectations and providing a more nuanced interpretation of the data.
+The slope ($\beta_1$) is particularly interesting, as it encapsulates the average annual decline in evaluation score attributable to aging.
+The Bayesian framework allows us to incorporate these hypotheses as priors in our model, aligning the analysis with our substantive expectations and providing a more nuanced interpretation of the data.
 
@@
 The above model equation serves as a predictive tool, estimating a building's evaluation score based on its age.
-In this equation, $y_i$ is the estimated evaluation score, $x_i$ represents the age of the building, $\varepsilon_i$ captures the residual effect—factors influencing the score that are not explained by the building's age.
-This implies that even among buildings of similar ages, scores can differ based on variables like maintenance quality, renovations, or compliance with updated building codes.
+In this equation, $y_i$ is the estimated evaluation score, $x_i$ represents the age of the building, and $\varepsilon_i$ captures the residual effect—factors influencing the score that is not explained by the building's age.
+This implies that scores can differ among buildings of similar ages based on variables like maintenance quality, renovations, or compliance with updated building codes.
 The equation recognizes that while age is a significant predictor, the complexity of real-world conditions means there's always an element of variability unexplained by age alone.
@@
 Displayed with building age on the x-axis and evaluation score on the y-axis, the data points represent individual apartment buildings.
-The blue line running through the cluster of points represents the linear regression line, which captures the average effect of age on evaluation score.
+The blue line running through the cluster of points represents the linear regression line, which captures the average effect of age on the evaluation score.
 Noticeably, the slope of the line is downward, suggesting a negative correlation; as the buildings get older, their evaluation scores tend to decrease.
@@
 
-This study embarked on a journey to understand the relationship between the age of apartment buildings in Toronto and their safety evaluation scores.
+This study aimed to understand the relationship between the age of apartment buildings in Toronto and their safety evaluation scores.
 Leveraging a dataset of 1,758 records from the Toronto Open Data portal, we employed simple linear regression analysis to unearth a significant inverse correlation between building age and safety scores.
 Specifically, our findings indicate that older buildings in Toronto tend to receive lower safety evaluation scores.
-This observation underscores the potential risks associated with aging infrastructure, aligning with the broader literature on building safety and maintenance.
+This observation underscores the potential risks associated with aging infrastructure, aligning with the broader building safety and maintenance literature.
 
@@
 Our analysis brings to light a critical insight into the urban infrastructure landscape: the aging of buildings could be a ticking time bomb if not properly managed.
-The negative correlation between building age and evaluation scores signals that older buildings may not meet current safety and maintenance standards compared to newer constructions.
+The negative correlation between building age and evaluation scores signals that older buildings may need to meet current safety and maintenance standards compared to newer constructions.
 This poses a significant challenge for city planners, policymakers, and building owners alike, emphasizing the need for regular inspections, maintenance, and renovations to ensure that these structures remain safe for occupancy.
@@
 
-In addition to previously mentioned limitations, the study examining the correlation between the age of apartment buildings in Toronto and their safety evaluation scores may face further constraints due to a variety of factors.
+In addition to the previously mentioned limitations, the study examining the correlation between the age of apartment buildings in Toronto and their safety evaluation scores may face further constraints due to various factors.
 One significant issue is sampling bias, where the dataset might not uniformly represent all building types, particularly if it disproportionately includes certain structures (such as residential over commercial) or concentrates on specific locales within Toronto, potentially leading to skewed outcomes.
@@
 These scores are determined by human evaluators, which introduces a subjective element to the assessment.
-Consequently, the scores might not accurately reflect the true condition of a building.
-Factors such as the evaluator's experience, training, and even their mood on the day of the evaluation can influence the scores assigned.
-Furthermore, inconsistencies in evaluation criteria or their application across different evaluators or buildings could lead to variability in scores that is not related to the actual condition of the buildings.
-This subjectivity and potential for inconsistency can introduce bias into our analysis, as the evaluation scores may not be a perfect representation of a building's safety and maintenance standards.
-It is important to consider these limitations when interpreting the results of our study and to approach the findings with cautio
+Consequently, the scores might not accurately reflect the actual condition of a building.
+Factors such as the evaluator's experience, training, and mood on the day of the evaluation can influence the scores assigned.
+Furthermore, inconsistencies in evaluation criteria or their application across different evaluators or buildings could lead to variability in scores unrelated to the actual condition of the buildings.
+This subjectivity and potential for inconsistency can introduce bias into our analysis, as the evaluation scores may not perfectly represent a building's safety and maintenance standards.
+It is essential to consider these limitations when interpreting the results of our study and to approach the findings with caution.
 
@@
 Next, the age of each building was calculated by subtracting the year it was built from the year it was evaluated, and this information was added to the dataset as a new column, AGE.
-The cleaned dataset, now free of missing values and containing the calculated ages, was saved as a CSV file in the 'analysis_data' directory for further analysis.
+The cleaned (analysis) dataset, now free of missing values and containing the calculated ages, was saved as a CSV file in the 'analysis_data' directory for further analysis.
 This thorough cleaning process was crucial for ensuring the reliability of the study's findings and laying a solid foundation for the statistical modeling that followed.
@@
 From @fig-posterior-plot, we observe that the simulated data from the posterior distribution (represented by the lighter lines) closely match the distribution of the observed data (depicted by the solid line).
-This suggests that our model has a good fit to the observed data and that the chosen priors and model structure can reasonably replicate the variations in evaluation scores across buildings.
-The spread of the lighter lines around the solid line also highlights the degree of uncertainty in our predictions, which is a natural aspect of modeling real-world phenomena.
+This suggests that our model is a good fit for the observed data and that the chosen priors and model structure can reasonably replicate the variations in evaluation scores across buildings.
+The spread of the lighter lines around the solid line also highlights the degree of uncertainty in our predictions, which is a natural aspect of modelling real-world phenomena.
 

### 2024-03-17 paper/datasheet.qmd
datasheet

---
title: "Datasheet for Toronto Apartment Building Evaluations 2023"
author: "Terry Tu, Jingyi Shen, Yaning Jin "
thanks: "Code and data are available at: https://github.com/TEJMaster/Toronto-Building-Safety-Analysis-2023"
date: today
date-format: long
abstract: "This study harnesses a dataset from the Toronto Open Data portal, comprising 1,758 records of apartment evaluations, to analyze the correlation between building age and safety scores. Employing a linear regression model, we discovered a significant inverse relationship, highlighting that older buildings tend to have lower safety evaluations. The findings suggest a need for policy reform, particularly in the maintenance and inspection of Toronto's aging residential infrastructure. Despite the study’s focus on building age, further research considering additional variables could offer a more comprehensive understanding of factors influencing building safety."
format: pdf
number-sections: true
bibliography: references.bib
link-citations: true
---

Extract of the questions from @gebru2021datasheets.

**Motivation**

1. *For what purpose was the dataset created? Was there a specific task in mind? Was there a specific gap that needed to be filled? Please provide a description.*
    - The dataset was created to monitor the safety and maintenance standards of Toronto's apartment buildings, with a focus on identifying how building age impacts safety evaluation scores.
2. *Who created the dataset (for example, which team, research group) and on behalf of which entity (for example, company, institution, organization)?*
    - The dataset was created by the City of Toronto as part of the RentSafeTO program.
3. *Who funded the creation of the dataset? If there is an associated grant, please provide the name of the grantor and the grant name and number.*
    - The dataset creation was funded by the City of Toronto.
4. *Any other comments?*
	- N/A

**Composition**

1. *What do the instances that comprise the dataset represent (for example, documents, photos, people, countries)? Are there multiple types of instances (for example, movies, users, and ratings; people and interactions between them; nodes and edges)? Please provide a description.*
	- The instances represent evaluations of apartment buildings, including their age and safety scores.
2. *How many instances are there in total (of each type, if appropriate)?*
	- There are 1,758 instances in the dataset.
3. *Does the dataset contain all possible instances or is it a sample (not necessarily random) of instances from a larger set? If the dataset is a sample, then what is the larger set? Is the sample representative of the larger set (for example, geographic coverage)? If so, please describe how this representativeness was validated/verified. If it is not representative of the larger set, please describe why not (for example, to cover a more diverse range of instances, because instances were withheld or unavailable).*
	- The dataset is a sample of all apartment buildings evaluated under the RentSafeTO program in Toronto. The representativeness of the sample was ensured by including a diverse range of buildings across different ages and geographic locations within the city.
4. *What data does each instance consist of? "Raw" data (for example, unprocessed text or images) or features? In either case, please provide a description.*
	- Each instance consists of features such as the building's age, year of evaluation, and safety evaluation score.
5. *Is there a label or target associated with each instance? If so, please provide a description.*
	- The target variable is the safety evaluation score, which indicates the building's compliance with safety standards.
6. *Is any information missing from individual instances? If so, please provide a description, explaining why this information is missing (for example, because it was unavailable). This does not include intentionally removed information, but might include, for example, redacted text.*
	- Some instances may have missing information due to incomplete records or unavailability of data at the time of evaluation.
7. *Are relationships between individual instances made explicit (for example, users' movie ratings, social network links)? If so, please describe how these relationships are made explicit.*
	- The dataset does not explicitly make relationships between individual instances.
8. *Are there recommended data splits (for example, training, development/validation, testing)? If so, please provide a description of these splits, explaining the rationale behind them.*
	- No specific data splits are recommended for this dataset.
9. *Are there any errors, sources of noise, or redundancies in the dataset? If so, please provide a description.*
	- The dataset may contain errors or noise due to inaccuracies in the evaluation process or inconsistencies in record-keeping.
10. *Is the dataset self-contained, or does it link to or otherwise rely on external resources (for example, websites, tweets, other datasets)? If it links to or relies on external resources, a) are there guarantees that they will exist, and remain constant, over time; b) are there official archival versions of the complete dataset (that is, including the external resources as they existed at the time the dataset was created); c) are there any restrictions (for example, licenses, fees) associated with any of the external resources that might apply to a dataset consumer? Please provide descriptions of all external resources and any restrictions associated with them, as well as links or other access points, as appropriate.*
	- Yes, possible link to [@rentsafeto] about the process taken to create the dataset. 
11. *Does the dataset contain data that might be considered confidential (for example, data that is protected by legal privilege or by doctor-patient confidentiality, data that includes the content of individuals' non-public communications)? If so, please provide a description.*
	- No.
12. *Does the dataset contain data that, if viewed directly, might be offensive, insulting, threatening, or might otherwise cause anxiety? If so, please describe why.*
	- No.
13. *Does the dataset identify any sub-populations (for example, by age, gender)? If so, please describe how these subpopulations are identified and provide a description of their respective distributions within the dataset.*
	- No.
14. *Is it possible to identify individuals (that is, one or more natural persons), either directly or indirectly (that is, in combination with other data) from the dataset? If so, please describe how.*
	- No.
15. *Does the dataset contain data that might be considered sensitive in any way (for example, data that reveals race or ethnic origins, sexual orientations, religious beliefs, political opinions or union memberships, or locations; financial or health data; biometric or genetic data; forms of government identification, such as social security numbers; criminal history)? If so, please provide a description.*
	- No.
16. *Any other comments?*
	- No.

**Collection process**

1. *How was the data associated with each instance acquired? Was the data directly observable (for example, raw text, movie ratings), reported by subjects (for example, survey responses), or indirectly inferred/derived from other data (for example, part-of-speech tags, model-based guesses for age or language)? If the data was reported by subjects or indirectly inferred/derived from other data, was the data validated/verified? If so, please describe how.*
	- The data for each instance was obtained through the City of Toronto's regulatory processes, where buildings are regularly evaluated to ensure they adhere to property standards. This information is observable and is reported by authorized city inspectors rather than being self-reported by subjects or derived from other data. This data was then validated through official city procedures to ensure accuracy and reliability.
2. *What mechanisms or procedures were used to collect the data (for example, hardware apparatuses or sensors, manual human curation, software programs, software APIs)? How were these mechanisms or procedures validated?*
	- The data collection involved administrative procedures by the City of Toronto, using software programs to aggregate and report the evaluations conducted by Bylaw Enforcement Officers. The collection methods are standardized according to city protocols to ensure consistent and valid data collection.
3. *If the dataset is a sample from a larger set, what was the sampling strategy (for example, deterministic, probabilistic with specific sampling probabilities)?*
	- The dataset is not a sample but a comprehensive collection of evaluations from the City of Toronto's Open Data portal. It reflects the information for all buildings that have undergone the evaluation process, representing a complete set within the city's database for a specified time frame.
4. *Who was involved in the data collection process (for example, students, crowdworkers, contractors) and how were they compensated (for example, how much were crowdworkers paid)?*
	- The data collection was conducted by the City of Toronto's municipal employees as part of their standard duties. No additional compensation was provided for data collection as it falls under their regular job responsibilities.
5. *Over what timeframe was the data collected? Does this timeframe match the creation timeframe of the data associated with the instances (for example, recent crawl of old news articles)? If not, please describe the timeframe in which the data associated with the instances was created.*
	- The data was collected over a period that aligns with the city's schedule for building evaluations. The exact time frame can be referenced from the dataset metadata, which would provide the dates of the evaluations.
6. *Were any ethical review processes conducted (for example, by an institutional review board)? If so, please provide a description of these review processes, including the outcomes, as well as a link or other access point to any supporting documentation.*
	- While specific ethical review processes for this dataset are not mentioned, it is assumed that the City of Toronto follows standard municipal practices for data collection, ensuring compliance with legal and ethical standards.
7. *Did you collect the data from the individuals in question directly, or obtain it via third parties or other sources (for example, websites)?*
	- The data was collected directly by the City of Toronto from building evaluations and is available to the public through the Toronto Open Data portal.
8. *Were the individuals in question notified about the data collection? If so, please describe (or show with screenshots or other information) how notice was provided, and provide a link or other access point to, or otherwise reproduce, the exact language of the notification itself.*
	-  In terms of notification and consent, given the regulatory nature of the data, individual building owners are typically aware of such evaluations, which are mandated by city bylaws. Consent is inherent in the regulatory process and is not required in the same way as it might be for personal data collection.
9. *Did the individuals in question consent to the collection and use of their data? If so, please describe (or show with screenshots or other information) how consent was requested and provided, and provide a link or other access point to, or otherwise reproduce, the exact language to which the individuals consented.*
	- The dataset does not involve personal data, so there is no mechanism for individuals to revoke consent for the use of this data as it is part of regulatory compliance.
10. *If consent was obtained, were the consenting individuals provided with a mechanism to revoke their consent in the future or for certain uses? If so, please provide a description, as well as a link or other access point to the mechanism (if appropriate).*
	- An impact analysis specifically for this dataset was not described, but it is part of the city's broader commitment to open data and transparent governance.
11. *Has an analysis of the potential impact of the dataset and its use on data subjects (for example, a data protection impact analysis) been conducted? If so, please provide a description of this analysis, including the outcomes, as well as a link or other access point to any supporting documentation.*
	- Additional comments or concerns about the data collection process can be directed to the City of Toronto's Open Data team through the contact details provided on the portal.
12. *Any other comments?*
	- No.

**Preprocessing/cleaning/labeling**

1. *Was any preprocessing/cleaning/labeling of the data done (for example, discretization or bucketing, tokenization, part-of-speech tagging, SIFT feature extraction, removal of instances, processing of missing values)? If so, please provide a description. If not, you may skip the remaining questions in this section.*
	- Yes, preprocessing and cleaning were performed on the dataset. We removed instances with missing values in the 'YEAR.BUILT', 'YEAR.EVALUATED', and 'CURRENT.BUILDING.EVAL.SCORE' columns to ensure completeness and reliability of the analysis. Additionally, a new variable 'AGE' was calculated as the difference between 'YEAR.EVALUATED' and 'YEAR.BUILT' to use as a predictor in our model.
2. *Was the "raw" data saved in addition to the preprocessed/cleaned/labeled data (for example, to support unanticipated future uses)? If so, please provide a link or other access point to the "raw" data.*
	- The original raw dataset remains stored in its initial directory labeled 'data/raw_data' within our project repository. This allows for reference or re-analysis should future research require access to the unprocessed information.
3. *Is the software that was used to preprocess/clean/label the data available? If so, please provide a link or other access point.*
	- The software used for preprocessing, namely the R programming language along with packages 'readr', 'dplyr', and 'here', is publicly available. The specific script used for cleaning is part of our project's repository on GitHub, which can be accessed via the provided link in the 'thanks' section of our paper.
4. *Any other comments?*
	- Following the cleaning process, we only retained the essential columns necessary for our analysis to streamline the dataset and focus on the variables of interest. The filtered dataset with these columns is available for review and further analysis, ensuring transparency and reproducibility of our study.

**Distribution**

1. *Will the dataset be distributed to third parties outside of the entity (for example, company, institution, organization) on behalf of which the dataset was created? If so, please provide a description.*
	- The dataset is distributed to the public under the City’s Open Government License, which allows for both commercial and non-commercial use without restrictions.
2. *How will the dataset be distributed (for example, tarball on website, API, GitHub)? Does the dataset have a digital object identifier (DOI)?*
	- The dataset can be downloaded directly from the City of Toronto Open Data Portal. While there is no mention of a DOI, the portal provides a direct download link for the dataset.
3. *When will the dataset be distributed?*
	- The dataset is already available for distribution as it is posted on the open data portal.
4. *Will the dataset be distributed under a copyright or other intellectual property (IP) license, and/or under applicable terms of use (ToU)? If so, please describe this license and/ or ToU, and provide a link or other access point to, or otherwise reproduce, any relevant licensing terms or ToU, as well as any fees associated with these restrictions.*
	- As mentioned, the dataset is distributed under the City’s Open Government License, which allows for worldwide, royalty-free, and perpetual use.
5. *Have any third parties imposed IP-based or other restrictions on the data associated with the instances? If so, please describe these restrictions, and provide a link or other access point to, or otherwise reproduce, any relevant licensing terms, as well as any fees associated with these restrictions.*
	-  No additional IP-based restrictions from third parties are imposed on the data, and there are no known export controls or other regulatory restrictions specific to the dataset.
6. *Do any export controls or other regulatory restrictions apply to the dataset or to individual instances? If so, please describe these restrictions, and provide a link or other access point to, or otherwise reproduce, any supporting documentation.*
	- For any additional questions or comments about the dataset, the Open Data team can be reached via their contact details on the portal.
7. *Any other comments?*
	- No

**Maintenance**

1. *Who will be supporting/hosting/maintaining the dataset?*
	- The City of Toronto's Open Data team will be responsible for supporting, hosting, and maintaining the dataset as part of their commitment to open government and data transparency.
2. *How can the owner/curator/manager of the dataset be contacted (for example, email address)?*
	- The Open Data team can be contacted through the City of Toronto's official open data portal, where contact information and a contact form are typically provided for inquiries and feedback.
3. *Is there an erratum? If so, please provide a link or other access point.*
	- Any errata or updates to the dataset are likely to be communicated through the City of Toronto Open Data Portal, where users can find the latest information and corrections.
4. *Will the dataset be updated (for example, to correct labeling errors, add new instances, delete instances)? If so, please describe how often, by whom, and how updates will be communicated to dataset consumers (for example, mailing list, GitHub)?*
	- The dataset is expected to be updated periodically by the City of Toronto's Open Data team to reflect new evaluations and corrections. Updates may be communicated through the Open Data Portal, newsletters, or official announcements.
5. *If the dataset relates to people, are there applicable limits on the retention of the data associated with the instances (for example, were the individuals in question told that their data would be retained for a fixed period of time and then deleted)? If so, please describe these limits and explain how they will be enforced.*
	- This dataset primarily relates to buildings and their evaluations, so it does not directly pertain to individuals. Therefore, retention limits specific to personal data may not be applicable.
6. *Will older versions of the dataset continue to be supported/hosted/maintained? If so, please describe how. If not, please describe how its obsolescence will be communicated to dataset consumers.*
	- Older versions of the dataset may be archived and accessible through the Open Data Portal. Any changes or discontinuation of support for older versions would likely be communicated through the portal or official channels.
7. *If others want to extend/augment/build on/contribute to the dataset, is there a mechanism for them to do so? If so, please provide a description. Will these contributions be validated/verified? If so, please describe how. If not, why not? Is there a process for communicating/distributing these contributions to dataset consumers? If so, please provide a description.*
	- While the City of Toronto encourages the use of open data, contributions to official datasets are typically managed by the responsible municipal teams. Any extensions or contributions would need to be coordinated with the Open Data team, and the validation process would depend on the nature of the contribution.
8. *Any other comments?*
	- The City of Toronto's Open Data initiative is committed to providing high-quality, accessible data to foster innovation, transparency, and informed decision-making. Users are encouraged to explore the available resources and engage with the Open Data team for any queries or suggestions.

\newpage

# References
